---
title: "leaflet_practice"
author: "Luke Vawter"
date: "October 18, 2018"
output: html_document
---
"Leaflet for R" is a helpful guide when working with leaflet:
https://rstudio.github.io/leaflet/json.html


a place to practice leaflet maps

```{r}
library(shiny)
library(leaflet)
library(dplyr)

df = read.csv("./cedr_phyto_station.csv", stringsAsFactors = F)

df$latitude <- as.numeric(df$latitude)
df$longitude <- as.numeric(df$longitude)

ui <- fluidPage(
    leafletOutput("mymap", height = 1000)
)

server <- function(input, output, session){
  
data <- reactive({
  x <- df
})
  
output$mymap <- renderLeaflet({
  m<-leaflet(data=df) %>%
    addTiles() %>%
    #setView(lng=73.935242, lat = 40.730610, zoom=10)
    addMarkers(lng= ~ longitude,
               lat= ~ latitude,
               popup = paste("Station", df$station, "<br>",
                             "Year:", df$stationdescription))
  m
})
}

shinyApp(ui = ui, server = server)
```

from a youtube tutorial
https://www.youtube.com/watch?v=07UB1lfHV-o :
```{r}
library(leaflet)
library(rgdal)

project.dir <- rprojroot::find_rstudio_root_file()

download.file("http://thematicmapping.org/downloads/TM_WORLD_BORDERS_SIMPL-0.3.zip",destfile = "TM_WORLD_BORDERS_SIMPL-0.3")

unzip("TM_WORLD_BORDERS_SIMPL-0.3.zip")

my_map = readOGR(dsn=getwd(), layer = "TM_WORLD_BORDERS_SIMPL-0.3")
# head(my_map)

# summary(my_map)
# 
# head(my_map$data)

leaflet(data = my_map) %>%
  addTiles() %>%
  setView(lat = 10, lng = 0, zoom = 2) %>%
  addPolygons(fillColor = "teal",
              highlight= highlightOptions(weight = 5,
                                          color="red",
                                          fillOpacity = .7,
                                          bringToFront = TRUE),
              label=my_map$NAME)

```

```{r}
library(shiny)
library(leaflet)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
library(rgdal)

project.dir <- rprojroot::find_rstudio_root_file()

# east.border <- readxl::read_excel(file.path(project.dir, "2018DREX_notes\data\Drought_Regions\eastern-region-border.shp"))


#file.path(project.dir, "2018DREX_notes\data\Drought_Regions")

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")
#head(eastern_region)
summary(eastern_region)
head(eastern_region$COUNTY)

#ereg <- spTransform(eastern_region, CRS("+init=epsg:4326"))

# county <- subset(eastern_region, COUNTY %in% c(
#   "CAROLINE","DORCHESTER","KENT","QUEEN ANNES","SOMERSET","TALBOT"
# ))

# leaflet(eastern_region) %>%
#   addTiles() %>%
#   setView(lng=-77.01293195597827, lat=38.987549813483675, zoom = 6) %>%
#   addPolygons(fillColor = "red",
#               highlight= highlightOptions(weight = 5,
#                                           color="blue",
#                                           fillOpacity = .7,
#                                           bringToFront = TRUE)#,
#               #label=eastern_region$COUNTY
# )



# leaflet(neStates) %>%
#   addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
#     opacity = 1.0, fillOpacity = 0.5,
#     fillColor = ~colorQuantile("YlOrRd", ALAND)(ALAND),
#     highlightOptions = highlightOptions(color = "white", weight = 2,
#       bringToFront = TRUE))

```

https://rstudio.github.io/leaflet/shapes.html
currently broken... to be continued:
```{r}
library(rgdal)

project.dir <- rprojroot::find_rstudio_root_file()

download.file("https://www.census.gov/geo/maps-data/data/cbf/cbf_state.html",destfile = "shp/cb_2013_us_state_20m.shp")

#unzip("cb_2017_us_state_500k.zip")

# From https://www.census.gov/geo/maps-data/data/cbf/cbf_state.html
states <- readOGR(dsn=getwd(), "shp/cb_2013_us_state_20m.shp",
  layer = "cb_2013_us_state_20m", GDAL1_integer64_policy = TRUE)

neStates <- subset(states, states$STUSPS %in% c(
  "CT","ME","MA","NH","RI","VT","NY","NJ","PA"
))

leaflet(neStates) %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5,
    fillColor = ~colorQuantile("YlOrRd", ALAND)(ALAND),
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE))
```



working template, rough non-functional scratch paper at the moment:
```{r}
library(shiny)
library(leaflet)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)

project.dir <- rprojroot::find_rstudio_root_file()

# east.border <- readxl::read_excel(file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions\\eastern-region-border.shp"))


map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}


erb = readOGR(dsn=map_path, layer = "eastern-region-border")



ui <- fluidPage(
    leafletOutput("mymap", height = 1000)
)

server <- function(input, output, session){
  
data <- reactive({
  x <- df
})
  
output$mymap <- renderLeaflet({
  m<-leaflet(data=df) %>%
    addTiles() %>%
    #setView(lng=73.935242, lat = 40.730610, zoom=10)
    addMarkers(lng= ~ longitude,
               lat= ~ latitude,
               popup = paste("Station", df$station, "<br>",
                             "Year:", df$stationdescription))
  m
})
}

shinyApp(ui, server)
```

using https://hautahi.com/rmaps to learn how to take a closer look at a shapefiles content.

inspection of all region shapefiles:
```{r}
library(shiny)
library(leaflet)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
library(rgdal)

project.dir <- rprojroot::find_rstudio_root_file()



map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")

eastern_region_border = readOGR(dsn=map_path, layer = "eastern-region-border")

clipsouthern3 = readOGR(dsn=map_path, layer = "clipsouthern3")

wssc_service = readOGR(dsn=map_path, layer = "wssc service")

clipcentral = readOGR(dsn=map_path, layer = "clipcentral")

baltimore_service = readOGR(dsn=map_path, layer = "baltimore service")


clipcentral_border = readOGR(dsn=map_path, layer = "clipcentral-border")

clipsouthern_border = readOGR(dsn=map_path, layer = "clipsouthern-border")

#eastern_region %>%
  #select(COUNTY) %>%
  #print()
  
eastern_region %>%
  #shows the bounding box which is the smallest rectangle that will hold all of the points
  bbox() #%>%

#this code prints the data( in dataframe) of the shapefile
head(eastern_region@data)
  
#this prints values in COUNTY column in data
print(eastern_region@data$COUNTY)

#This plots the region polygon
plot(eastern_region); title(main = list("Maryland eastern region "), cex=0.8)

plot(eastern_region_border); title(main = list("Maryland eastern region border"), cex=0.8)

plot(clipsouthern3); title(main = list("Maryland clipsouthern3"), cex=0.8)


plot(wssc_service); title(main = list("Maryland wssc service"), cex=0.8)

plot(clipcentral); title(main = list("Maryland clipcentral"), cex=0.8)

plot(baltimore_service); title(main = list("Maryland baltimore service"), cex=0.8)

plot(clipcentral_border); title(main = list("Maryland clipcentral"), cex=0.8)

plot(clipsouthern_border); title(main = list("Maryland clipsouthern-border"), cex=0.8)




```

```{r}

library(shiny)
library(leaflet)
library(dplyr)
library(choroplethr)
library(choroplethrMaps)
library(rgdal)
library(sp)

project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")


clipsouthern3 = readOGR(dsn=map_path, layer = "clipsouthern3")


CRS(eastern_region)
# proj4string(eastern_region)<-CRS("+init=epsg:4326")

#transform the projection of esatern_region
# eastern_region <- spTransform(eastern_region, CRS("+init=epsg:4326"))

#leaflet(eastern_region)
```


so now that I know what I'm doing, let's try the census exercise again. Got it working and also changed states to local states:
```{r}
library(rgdal)

# From https://www.census.gov/geo/maps-data/data/cbf/cbf_state.html
states <- readOGR("shp/cb_2013_us_state_20m.shp",
  layer = "cb_2013_us_state_20m", GDAL1_integer64_policy = TRUE)

neStates <- subset(states, states$STUSPS %in% c(
  "CT","ME","MA","NH","RI","VT","NY","NJ","PA"
))

oStates <- subset(states, states$STUSPS %in% c(
  "MD","VA","WV","PA"
))

leaflet(oStates) %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 1.0,#0.5,
    fillColor = ~colorQuantile("YlOrRd", ALAND)(ALAND),
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE))

typeof(head(states@data$STUSPS))
print(states)
```

```{r}
library(leaflet)
library(rgdal)


project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")

head(eastern_region@data)

er_counties <- subset(eastern_region, eastern_region$REGION %in% c(
  "Eastern"#"WICOMICO", "KENT"
))

leaflet(eastern_region) %>% #er_counties) %>%
  addPolygons(color = "#444444", weight = 1, smoothFactor = 0.5,
    opacity = 1.0, fillOpacity = 0.5,
    #fillColor = ~colorQuantile("YlOrRd", CENSCNTY_I)(CENSCNTY_I),
    highlightOptions = highlightOptions(color = "white", weight = 2,
      bringToFront = TRUE))
```

```{r}
library(leaflet)
library(rgdal)


project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")

clipcentral = readOGR(dsn=map_path, layer = "clipcentral")

leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolygons(data=eastern_region, fillOpacity = 0.7,weight = 1.2, color="RED") %>%
  addPolygons(data=clipcentral, fillOpacity = 0.7,weight = 1.2, color="BLUE")
```

```{r}
library(leaflet)
library(rgdal)
library(raster)
project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")

clipcentral = readOGR(dsn=map_path, layer = "clipcentral")

crs(eastern_region)
crs(eastern_region) <- CRS("+proj=longlat +datum=WGS84")
crs(eastern_region)

#print(eastern_region)


# eastern_region2 <- spTransform(eastern_region, CRS("+init=epsg:4326"))
# 
# leaflet(eastern_region2)
```
so we have an NA crs value :(s)


http://rspatial.org/spatial/rst/6-crs.html
this is how to find a projection for a given region:
```{r}
library(rgdal)
epsg <- make_EPSG()
i <- grep("Maryland", epsg$note, ignore.case=TRUE)

epsg[i[1:3], ]


```

```{r}
library(shiny)
library(leaflet)
library(dplyr)
library(rgdal)

project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

eastern_region = readOGR(dsn=map_path, layer = "eastern-region")



print(eastern_region)
print(eastern_region@proj4string)
summary(eastern_region)
```
class       : SpatialPolygonsDataFrame
extent      : 454148.2, 570301.2, 27991.99, 191141.5  (xmin, xmax, ymin, ymax)
coord. ref. : NA 

CRS arguments: NA 






```{r}
library(ggplot2)
library(leaflet)
library(rgdal)
library(raster)

#project directory, followed by path to shapefiles
project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

###maryland map regions
eastern_region = readOGR(dsn=map_path, layer = "eastern-region")

eastern_region_border = readOGR(dsn=map_path, layer = "eastern-region-border")

clipsouthern3 = readOGR(dsn=map_path, layer = "clipsouthern3")

wssc_service = readOGR(dsn=map_path, layer = "wssc service")

clipcentral = readOGR(dsn=map_path, layer = "clipcentral")

baltimore_service = readOGR(dsn=map_path, layer = "baltimore service")

clipcentral_border = readOGR(dsn=map_path, layer = "clipcentral-border")

clipsouthern_border = readOGR(dsn=map_path, layer = "clipsouthern-border")

#outputs shapefile data for structure comparison purposes before merging
# head(eastern_region@data)
# head(clipcentral@data)
# head(wssc_service@data)
# head(baltimore_service@data)
# head(clipsouthern3@data)

#drops extra columns off of a copy of region shapefile so that it can be joinned with MD-regions file below
drops <- c("ID","SOURCETHM", "HECTARES", "CENSCNTY_","CENSCNTY_I", "FIPS", "COUNTY", "REGION") # list of col names
clipcentral2 <- clipcentral[,!(names(clipcentral) %in% drops)]

eastern_region2 <- eastern_region[,!(names(eastern_region) %in% drops)]

clipsouthern3_2 <- clipsouthern3[,!(names(clipsouthern3) %in% drops)]

wssc_service2 <- wssc_service[,!(names(wssc_service) %in% drops)]

baltimore_service2 <- baltimore_service[,!(names(baltimore_service) %in% drops)]

# head(eastern_region2@data)
# head(clipcentral2@data)
# head(wssc_service2@data)
# head(baltimore_service2@data)
# head(clipsouthern3_2@data)


#joins regions into one file
MD_regions <- rbind(eastern_region2,clipcentral2,baltimore_service2,wssc_service2,clipsouthern3_2)

plot(MD_regions)
summary(MD_regions)

class(MD_regions)
names(MD_regions)

# m <- leaflet(MD_regions)

# m <- leaflet(MD_regions) %>%
#   setView(-96, 37.8, 4) %>%
#   addProviderTiles("MapBox", options = providerTileOptions(
#     id = "mapbox.light",
#     accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
# m
```
 so we have an output of the merged shapefiles(border files not currently included).  For some reason we have no western region shapefile(ask Cherie and Heidi).  We also may have the issue of not being able to easily chnage the background color of each region now that they are merged.  Also, plotting in leaflet rather than base R plot() function would be ideal.  Still, this is a start and gives us something to play with.  Difficulties with the shapefile include not knowing the crs, and its coords being in a slot: [x,y] structure rather than lat, long columns.  Other stuff I'm not thinking about as well.  The format's not ideal for what I'm trying to do, but I still think we cna find a way to make it work with more fiddling.  More to do, but a good way to end the week.

```{r}

library(ggplot2)
library(leaflet)
library(rgdal)
library(raster)
library(sp)
library(spdplyr)

#project directory, followed by path to shapefiles
project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}

western_central = readOGR(dsn=map_path, layer = "western_central")

clipcentral = readOGR(dsn=map_path, layer = "clipcentral")

western_dslv = readOGR(dsn=map_path, layer = "western_dslv")

# proj4string(western_central)
# # proj4string(western_central)<-CRS("+init=epsg:2248")#26985")
# # proj4string(western_central)
# plot(western_central)

western_central_t <- spTransform(western_central, CRS("+init=epsg:4326"))

clipcentral_t <- spTransform(clipcentral, CRS("+init=epsg:4326"))

western_region_t <- spTransform(western_dslv, CRS("+init=epsg:4326"))

head(western_central)
summary(western_central)
head(western_central)

# western_central_t <- western_central_t %>%
#   select(western_central_t$REGION[0])

c_color="blue"
w_color="red"

m <- leaflet() %>%
  # addPolygons(data = western_central_t, color=color) #%>%
  
  addPolygons(data = clipcentral_t, color="black", fillColor = c_color, opacity = 1) %>%
  addPolygons(data = western_region_t, color="black", fillColor = w_color, opacity = 1)

  # fillColor = ~pal(density),
  # weight = 2,
  # opacity = 1,
  # color = "white",
  # dashArray = "3",
  # fillOpacity = 0.7)

m


```

Data attributes:
     REGION 
 Central:1  
 Western:1  
   REGION
0 Western
1 Central

```{r}
library(geojsonio)
library(geojson)
library(sp)
library(jsonlite)
library(leaflet)



states <- geojsonio::geojson_read("json/us-states.geojson", what = "sp")


m <- leaflet(states) %>%
  setView(-96, 37.8, 4) %>%
  addProviderTiles("MapBox", options = providerTileOptions(
    id = "mapbox.light",
    accessToken = Sys.getenv('MAPBOX_ACCESS_TOKEN')))
```



<<<<<<< HEAD
=======
https://blog.exploratory.io/creating-geojson-out-of-shapefile-in-r-40bc0005857d:
```{r}
library(rgdal)
library(spdplyr)
library(geojsonio)
library(rmapshaper)
library(leaflet)
library(jsonlite)

project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "2018DREX_notes\\data\\Drought_Regions")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "2018DREX_notes/data/Drought_Regions")}


eastern_region = readOGR(dsn=map_path, layer = "eastern-region")

head(eastern_region@data )

#this code uses spdplyr, an amazing package which allows you to manipulate spatial dataframes like any other dataframe in R
eastern_region_modified <- eastern_region %>%
  select(AREA, PERIMETER)
  
eastern_region_modified



eastern_region_modified.json <- geojson_json(eastern_region_modified)

leaflet() %>% addGeoJSON(eastern_region_modified.json)
#leaflet(data=eastern_region_modified.json)

#print(paste("geojson data: ", eastern_region_modified.json))

erm_json_simplified <- ms_simplify(eastern_region_modified.json)


```

```{r}
library(geojsonio)
project.dir <- rprojroot::find_rstudio_root_file()

map_path <- file.path(project.dir, "Practice//")

if( .Platform$OS.type == "unix" ) {map_path <- file.path(project.dir, "Practice/")}


allcounties <- geojsonio::geojson_read(paste0(map_path,"gz_2010_us_050_00_500k.json"), #"json/nycounties.geojson",
  what = "sp")

pal <- colorNumeric("viridis", NULL)

leaflet(allcounties)
  # addTiles() %>%
  # addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
  #   fillColor = "red") #~pal(log10(pop)),
  #   label = ~paste0(county, ": ", formatC(pop, big.mark = ","))) %>%
  # addLegend(pal = pal, values = ~log10(pop), opacity = 1.0,
  #   labFormat = labelFormat(transform = function(x) round(10^x)))
```

>>>>>>> a22c4999bb5df531786cce3fd4da7d3fd1d6425e


```{r}
library(dplyr)
library(jsonlite)
library(leaflet)

#-----------------required variables and functions-----------------
todays.date <- format(Sys.Date(), "%m-%d-%Y")
min_date = "01-01-2018"
max_date = todays.date
CEDR_url <- "http://datahub.chesapeakebay.net/api.JSON"

phyto_num = "17"
SPCOND = 94

clean_string <- function(dataframe) {
  dataframe %>% 
    stringr::str_trim() %>% 
    tolower() %>% 
    stringr::str_replace_all("\\s+", " ") %>% 
    stringr::str_replace_all(" ", "_") %>%  
    if_else(. == "", as.character(NA), .)
}

clean_up <- function(dataframe) {
  dataframe %>% 
    rename_all(clean_string) %>% 
    mutate_if(is.character, funs(clean_string))%>% 
    distinct()
}
#--------------------------------------------------------


#-----create a station vector for us in data pull------
#temporary placement
station.vec <- file.path(CEDR_url,
                         "LivingResources",
                         "TidalPlankton",
                         "Reported",
                         min_date,
                         max_date,
                         phyto_num,
                         "Station") %>%
  fromJSON() %>%
  pull(unique(MonitoringLocationId))


#-------------this is a temporary data pull for gettting data with stations so i have point data to show off leaflet
data.df <- file.path(CEDR_url,
                                                 "WaterQuality",
                                                 "WaterQuality",
                                                 
                                                 min_date,
                                                 max_date,
                                                 "6",  #programIds
                                                 "7,23",#"7,16,23,24",  #projectIds
                                                 "station",
                                                 paste(station.vec, collapse = ","),
                                                 paste(
                                                   #these are the parameter variables declared in Functions and Variables section
                                                   SPCOND
                                                   , sep=",")) %>%
  fromJSON() %>%
  clean_up() 

leaflet(data =data.df) %>%
      addMarkers(lng= ~ longitude,
               lat= ~ latitude)
```


write new pull to file
```{r}

library(shiny)
library(shinythemes)
library(shinydashboard)
library(tidyverse)
library(dplyr)
library(jsonlite)
library(ggplot2)
library(rlang)
library(data.table)
library(stringi)
library(Cairo)
library(RcppRoll)
library(tidyr)
library(lubridate)
library(pryr)
library(zoo)
library(sp)
library(leaflet)
library(rgdal)
library(RCurl)
library(curl)

#-----------------required variables and functions-----------------
todays.date <- format(Sys.Date(), "%m-%d-%Y")
min_date = "01-01-2018"
max_date = todays.date
CEDR_url <- "http://datahub.chesapeakebay.net/api.JSON"
data_path <- "data/CEDR/"

phyto_num = "17"
SPCOND = 94
MAIN = 7 #Tidal Mainstem Water Quality Monitoring Project
TRIB = 23 #Tidal Tributary Water Quality Monitoring Project

clean_string <- function(dataframe) {
  dataframe %>% 
    stringr::str_trim() %>% 
    tolower() %>% 
    stringr::str_replace_all("\\s+", " ") %>% 
    stringr::str_replace_all(" ", "_") %>%  
    if_else(. == "", as.character(NA), .)
}

clean_up <- function(dataframe) {
  dataframe %>% 
    rename_all(clean_string) %>% 
    mutate_if(is.character, funs(clean_string))%>% 
    distinct()
}
#--------------------------------------------------------

#----------------water quality parameters-----------------------
CLW =23
DIN = 30
DO = 31
DOC = 34
DON = 35
DOP = 36
NH4F = 60
NO23F = 63
NO2F = 65
PC =  71
PH = 73
PN =  77
PO4F = 78
PP =82
SALINITY = 83
SIGMA_T = 88
SO4W = 93
SPCOND = 94
TALK = 100
TDN = 104
TDP = 105
TN = 109
TON = 111
TP = 114
TSS = 116
TURB_NTU = 119
WTEMP = 123
#----------------------------------------------------------------

#-------------------location vector-------------------
huc8.vec <- file.path(CEDR_url,
                         "LivingResources",
                         "TidalPlankton",
                         "Reported",
                         min_date,
                         max_date,
                         phyto_num,
                         #"Station"
                         "Huc8"
                         ) %>%
  fromJSON() %>%
  pull(unique(HUCEightId))
    #MonitoringLocationId
#---------------------------------------------------

#---------------------data pull------------------------------------
        plot_data.df <- file.path(CEDR_url,
                                  "WaterQuality",
                                  "WaterQuality",
                                  
                                  min_date,
                                  max_date,
                                  "6",  #programIds
                                  paste(
                                          #these are the parameter variables declared in Functions and Variables section
                                          MAIN,TRIB
                                          , sep=","),#"7,16,23,24",  #projectIds
                                  "Huc8",
                                  paste(huc8.vec, collapse = ","),
                                  paste(
                                          #these are the parameter variables declared in Functions and Variables section
                                          CLW, DIN, DO, DOC, DON, DOP, NH4F, NO23F, NO2F, PC, PH, PN, PO4F, PP, SALINITY, SIGMA_T, SO4W, SPCOND, TALK, TDN, TDP, TN, TON, TP, TSS, TURB_NTU, WTEMP
                                          , sep=",")
        ) %>%
                fromJSON() %>%
                clean_up() %>%

write_csv(., paste0(data_path, "cedr_wq_tweak.csv"))
#data.table::fwrite(file.path(project.dir, data_path, "cedr_wq_tweak.csv"))
#-------------------------------------------------------------------

```


```{r}
# 
library(shiny)
library(leaflet)
library(dplyr)

data_path <- "data/CEDR/"
# 
# df = read.csv("./cedr_phyto_station.csv", stringsAsFactors = F)
# 
# df$latitude <- as.numeric(df$latitude)
# df$longitude <- as.numeric(df$longitude)
# 

#read file
map_data.df <- data.table::fread(paste0(data_path, "cedr_wq_tweak.csv"),
                                  header = TRUE,
                                  data.table = FALSE) %>%
    filter(parameter == "spcond")

map_data.df$latitude <- as.numeric(map_data.df$latitude)
map_data.df$longitude <- as.numeric(map_data.df$longitude)


ui <- fluidPage(
    leafletOutput("mymap", height = 1000)
)
# 
server <- function(input, output, session){
#   
data <- reactive({
  x <- map_data.df
})
#   
output$mymap <- renderLeaflet({
  m<-leaflet(data=map_data.df) %>%
    addTiles() %>%
    #setView(lng=73.935242, lat = 40.730610, zoom=10) %>%
    setView(lng=-77.01293195597827, lat=38.987549813483675, zoom = 12) %>%
    addMarkers(lng= ~ longitude,
               lat= ~ latitude,
               popup = paste("Station", map_data.df$station, "<br>",
                             "Year:", map_data.df$stationdescription)
               )
  m
})
}
# 
shinyApp(ui = ui, server = server)
```

```{r}

library(shiny)
library(leaflet)
library(dplyr)

df = read.csv("./cedr_phyto_station.csv", stringsAsFactors = F)

df$latitude <- as.numeric(df$latitude)
df$longitude <- as.numeric(df$longitude)

ui <- fluidPage(
    leafletOutput("mymap", height = 1000)
)

server <- function(input, output, session){
  
data <- reactive({
  x <- df
})
  
output$mymap <- renderLeaflet({
  m<-leaflet(data=df) %>%
    addTiles() %>%
    #setView(lng=73.935242, lat = 40.730610, zoom=10)
    addMarkers(lng= ~ longitude,
               lat= ~ latitude,
               popup = paste("Station", df$station, "<br>",
                             "Year:", df$stationdescription))
  m
})
}

shinyApp(ui = ui, server = server)

```

