---
title: "R_practice2.Rmd"
output: html_document
---
note:continued from R-practice.Rmd


to test RET,TF,LE station issue fix
```{r}
library(dplyr)
library(readxl)
library(data.table)

project.dir <- rprojroot::find_rstudio_root_file()

events_test.df <- data.table::fread(file.path(project.dir, 
                                                 "data/phytoplankton2/VA_ODU_phyto_event.csv"),
                            data.table = FALSE,
                            #colClasses = col.class.vec,
                            na.strings = "")

stations_test.df <- events_test.df %>%
  select(station) %>%
  distinct()

events_test.df <- events_test.df%>%

mutate(salzone_test = case_when(
    events_test.df$station %in% c("tf3.3","tf4.2","tf5.5")~ "F",
    #events_test.df$station == starts_with("cb")~ "good",
    events_test.df$station %in% c("ret3.1","ret4.3","ret3.1")~ "O",
    events_test.df$station %in% c("le3.6","le5.2","le5.4","le5.5-w")~ "P",
    TRUE~"bogus"

  )
  )

    

```

```{r}
library(dplyr)
library(readxl)
library(data.table)

project.dir <- rprojroot::find_rstudio_root_file()

taxa.df <- data.table::fread(file.path(project.dir, 
                                                 "data/phytoplankton2/VA_ODU_phyto_taxa.csv"),
                            data.table = FALSE,
                            #colClasses = col.class.vec,
                            na.strings = "")



id <- c(1,2,3)
date <- c("1/1/1","2/2/2","3/3/3")
name <- c("ted","fred", "dave")
value <- c(12,5,10)
data.df <- data.frame(id, date, value, name)

n.df <- data.df%>%
  group_by_at(vars(-value)) %>% 
  summarise(value=mean(value)) %>%
  ungroup()


#count(data.df$name == 23)

test.df <- data.df %>% 
  group_by_at(vars(-value)) %>%
  summarize(value = sum(value)) %>%
  ungroup()

find.df <- data.df %>%
  filter(grepl("ed", name))

# test2.df <- taxa.df %>% 
#   group_by_at(vars(-reportingvalue)) #%>%
  # summarize(reportingvalue2 = sum(reportingvalue)) %>%
  # ungroup()


```


this is salzone calculation but without 3 day
```{r}
library(dplyr)
library(readxl)
library(data.table)
library(tidyr)

project.dir <- rprojroot::find_rstudio_root_file()
wq.raw <- data.table::fread(file.path(project.dir, "data/water_quality/cedr_wq.csv"),
                            data.table = FALSE,
                           na.strings = c("")) %>% 
  filter(is.na(problem),
         parameter %in% c("chla", "doc", "pheo", "salinity"))

wq.df <- wq.raw %>% 
  mutate(sampledate = as.Date(sampledate))

wq.df <- wq.df %>% 
  select(station, source, sampledate, samplereplicatetype,
         depth, layer, 
         #pycnocline, upperpycnocline, lowerpycnocline,
         parameter, measurevalue) %>% 
  distinct()

wq.df <- wq.df %>% 
  filter(layer == "s", 
         parameter == "chla") %>% 
  unite(parameter, c("layer", "parameter"), remove = FALSE) %>% 
  bind_rows(wq.df)

chla <- wq.df %>%
  filter(parameter=="chla")

#get event.df
events.df <- data.table::fread(file.path(project.dir, "data/phytoplankton2/VA_ODU_phyto_event.csv"
                                         ),
                            data.table = FALSE,
                            na.strings = "")

#get pdepth from event.df
pdepth.df <- events.df %>% 
  filter(layer %in% c("ap", "wc")) %>% 
  mutate(sampledate = as.Date(sampledate)) %>% 
  select(station, sampledate, pdepth) %>% 
  dplyr::distinct()

#filter out below pdepth samples in wq.df
wq.df <- left_join(wq.df, pdepth.df, by = c("station", "sampledate"))
wq.df <- wq.df %>% 
  filter(depth <= pdepth) #%>% 
  
s_chla.df <- wq.df %>%
  filter(parameter=="s_chla")


di_doc.df <- wq.df %>%
  filter(parameter=="doc")

di_chla <- wq.df %>%
  filter(parameter == "chla")

di_salinity <- wq.df %>%
  filter(parameter == "salinity")

di_pheo <- wq.df %>%
  filter(parameter == "pheo")

avg_sal.df <- di_salinity %>%

  group_by(station, sampledate) %>%
  mutate(avg_sal = mean(measurevalue, na.rm = TRUE)) %>%
  ungroup()

avg_salzone.df <- avg_sal.df %>%

  mutate(salzone = case_when(
    measurevalue >0 & measurevalue <= 0.5 ~ "F",
    measurevalue > .5 &  measurevalue <= 5 ~ "O",
    measurevalue > 5 & measurevalue <= 18 ~ "M",
    measurevalue > 18~ "P")
  )
```

```{r}
library(dplyr)
library(readxl)
library(data.table)
library(tidyr)

project.dir <- rprojroot::find_rstudio_root_file()

wq.raw <- data.table::fread(file.path(project.dir, "data/water_quality/cedr_wq.csv"),
                            data.table = FALSE,
                           na.strings = c("")) %>% 
  filter(is.na(problem),
         parameter %in% c("chla", "doc", "pheo", "salinity"))


events.df <- data.table::fread(file.path(project.dir, "data/phytoplankton2/VA_ODU_phyto_event.csv"
                                         ),
                            data.table = FALSE,
                            na.strings = "")

wq.df <- wq.raw %>% 
  mutate(sampledate = as.Date(sampledate))

#3 day prep
events.sub <- events.df %>% 
  select(station, sampledate) %>% 
  distinct() %>% 
  mutate(sampledate = as.Date(sampledate)) %>%
  mutate(lower_date = sampledate - lubridate::days(3),
         upper_date = sampledate + lubridate::days(3))

library(parallel)
n.cores <- detectCores() - 1
cl <- makeCluster(n.cores)
clusterExport(cl = cl, varlist = c("wq.df", "events.sub"))
clusterEvalQ(cl, c(library(dplyr))) %>% invisible()

env.df <- parLapply(cl, 1:nrow(events.sub), function(row.i) {
  
  sub.df <- slice(events.sub, row.i)
  #----------------------------------------------------------------------------
  sub.env <- wq.df %>% 
    filter(station == sub.df$station,
           date >= sub.df$lower_date,
           date <= sub.df$upper_date)
  #----------------------------------------------------------------------------
  if (nrow(sub.env) == 0) return(data.frame(
    station = NA,
    date = NA,
    parameter = NA,
    measurevalue = NA
  ))
  #----------------------------------------------------------------------------
  final.df <- sub.env %>% 
    mutate(date_diff = date - sub.df$sampledate,
           abs_date_diff = abs(date_diff),
           sampledate = sub.df$sampledate) %>% 
    filter(abs_date_diff == min(abs_date_diff))
  #----------------------------------------------------------------------------
  if (nrow(final.df) > 1) {
    final.df <- final.df %>% 
      filter(date == min(date))
  }
  #----------------------------------------------------------------------------
  return(final.df)
}) %>% 
  bind_rows() %>% 
  filter(!is.na(station))

stopCluster(cl)
```

```{r}
library(dplyr)
library(readxl)
library(data.table)
library(tidyr)

project.dir <- rprojroot::find_rstudio_root_file()

wq.raw <- data.table::fread(file.path(project.dir, "data/water_quality/cedr_wq.csv"),
                            data.table = FALSE,
                           na.strings = c("")) %>% 
  filter(is.na(problem),
         parameter %in% c("chla", "doc", "pheo", "salinity"))


events.df <- data.table::fread(file.path(project.dir, "data/phytoplankton2/VA_ODU_phyto_event.csv"
                                         ),
                            data.table = FALSE,
                            na.strings = "")

wq.df <- wq.raw %>% 
  mutate(sampledate = as.Date(sampledate))

wq.df <- wq.df %>% 
  select(station, source, sampledate, samplereplicatetype,
         depth, layer, 
         #pycnocline, upperpycnocline, lowerpycnocline,
         parameter, measurevalue) %>% 
  distinct()

#get pdepth from event.df
pdepth.df <- events.df %>% 
  filter(layer %in% c("ap", "wc")) %>% 
  mutate(sampledate = as.Date(sampledate)) %>% 
  select(station, sampledate, pdepth) %>% 
  dplyr::distinct()

#filter out below pdepth samples in wq.df
wq.df <- left_join(wq.df, pdepth.df, by = c("station", "sampledate"))
wq.df <- wq.df %>% 
  filter(depth <= pdepth) #%>% 

#3 day prep
events.sub <- events.df %>% 
  select(station, sampledate) %>% 
  distinct() %>% 
  mutate(sampledate = as.Date(sampledate)) %>%
  mutate(lower_date = sampledate - lubridate::days(3),
         upper_date = sampledate + lubridate::days(3))

library(parallel)
n.cores <- detectCores() - 1
cl <- makeCluster(n.cores)
clusterExport(cl = cl, varlist = c("wq.df", "events.sub"))
clusterEvalQ(cl, c(library(dplyr))) %>% invisible()

env.df <- parLapply(cl, 1:nrow(events.sub), function(row.i) {
  
  sub.df <- slice(events.sub, row.i)
  #----------------------------------------------------------------------------
  sub.env <- wq.df %>%
    filter(station == sub.df$station,
           date >= sub.df$lower_date,
           date <= sub.df$upper_date)
  
  return(sub.df)
})
```

```{r}
bay.sub <- bay.df %>% 
  select(station, sampledate) %>% 
  distinct() %>% 
  mutate(sampledate = as.Date(sampledate)) %>%
  mutate(lower_date = sampledate - lubridate::days(3),
         upper_date = sampledate + lubridate::days(3))
```

```{r}
foo <- local({x <- 10
             y <- 200
             x +y})

foo

x <- 4

z <- rlang::expr(y <- x * 10)
eval(z)
y


```

```{r}

library(dplyr)


prop_count <- function(df, ...){
  vars_col <- quos(...)
  
  print(vars_col)
  
  df %>% 
    count(!!!vars_col, sort = T) %>% 
    mutate(prop_n = prop.table(n)) %>% 
    mutate(cumsum_n = cumsum(prop_n)) 
}

dplyr::starwars %>% 
  prop_count(homeworld, species)
```
```{r}
var <- 12
range.vec <- c(1:var)
print(range.vec)
```
```{r}
library(dplyr)
set.seed(0)

#Dummy data.frame to test
df <- tbl_df(data.frame(x = rep(1:3, each = 4)))

#Generate the random integer column
df_test = df %>% 
  rowwise() %>%
  mutate(pop=sample(0:1, 1, replace=TRUE))
```

```{r}
# library(dplyr)
# library(readxl)
# library(data.table)
# library(tidyr)
# 
# project.dir <- rprojroot::find_rstudio_root_file()
# 
# event.df <- data.table::fread(file.path(project.dir, "data/phytoplankton2/VA_ODU_phyto_event.csv"
#                                          ),
#                             data.table = FALSE,
#                             na.strings = "")
# 
# 
# test.df <- lapply(1:nrow(event.df), function(row.i)) {
#   
# }

```

```{r}
library(dplyr)

count_var <-  97

id_df <- c(1,2,3,4,5)
var_df <- c(0,0,0,0,0)
my_var <-  c(97,97,97,97,97)
#my_var <- c(100,100,100,100,100)
value_df <- c(0,1,0,1,1)
data.df <- data.frame(id_df,my_var, value_df)


###########  this is it
while((sum(subset(data.df$my_var,value_df !=0)) / as.numeric(nrow(subset(data.df,value_df >0))))<100){

data.df <-data.df %>%
mutate(my_var = case_when( my_var < 100 & value_df >0 ~my_var + 1, TRUE ~ my_var))
}
###########



# rows <-  as.numeric(nrow(subset(data.df,value_df >0)))
# total <- (sum(data.df$my_var) / nrow(data.df - as.numeric(nrow(subset(data.df,value_df >0)))))
# 
# # while((sum(data.df$my_var) / nrow(data.df - nrow(data.df$value.df==0))) <100) {
# apple <- sum(subset(data.df$my_var,value_df !=0)) / as.numeric(nrow(subset(data.df,value_df >0)))# - as.numeric(sum(subset(data.df$my_var,value_df ==0))))
# 
# while((sum(subset(data.df$my_var,value_df !=0)) / as.numeric(nrow(subset(data.df,value_df >0))))<100){
# 
# data.df <-data.df %>%
# mutate(my_var = case_when( my_var < 100 & value_df >0 ~my_var + 1, TRUE ~ my_var))
# }
#while((sum(data.df$my_var) / nrow(data.df - as.numeric(nrow(subset(data.df,value_df ==0))))) <100) {
    # my_var <- my_var + 1
    # print("one more time")
    
    # mutate(my_var = my_var + value_df, count_var <- countvar + case_when(value_df > 0~, TRUE <- 0))
    



```


```{r}
library(dplyr)
library(ggplot2)

project.dir <- rprojroot::find_rstudio_root_file()

dir.create(file.path(project.dir, "data/"),
           recursive = TRUE, showWarnings = FALSE)

#fill in blank with dataframe name
#data.table::fwrite(__________, file.path(project.dir, "data/", "SprBIBI.csv"))



BIBI_plot.df <- data.table::fread(file.path(project.dir, 
                                                 "data/SprBIBI.csv"),
                            data.table = FALSE,
                            #colClasses = col.class.vec,
                            na.strings = "")

BIBI_plot.df <- BIBI_plot.df %>%
  mutate(SITE = as.character(SITE))



plot_df <-BIBI_plot.df %>% group_by(LOCATION) %>%
  do(
    plots =ggplot(data = .) + aes(x = SITE, y = BIBI) +
      geom_boxplot() + ggtitle(.$LOCATION)
  )

plot_df$plots

###############################
counter = 0
for(item in plot_df$plots) {
  counter = counter + 1
  ggsave(filename = paste0("plot",counter), plot = p[[counter]], device= "pdf")
  print(item)
}
##############################

p <- plot_df$plots

p[[1]]
ggsave(filename = paste0("plot",counter), plot = p[[1]], device= "pdf")


#myplot <- ggplot(mtcars, aes(wt, mpg)) + geom_point()
# print(myplot)
# dev.off()

#pdf("plot_df", width = 10)

# 
# BIBI_plot.df <- BIBI_plot.df %>%
#   group_by(LOCATION, SITE) %>%
#   do(ggplot(data = BIBI_plot.df, aes(SITE,BIBI, group = LOCATION))) %>%
#   ungroup()
# 
# ggplot(data = BIBI_plot.df, aes(SITE,BIBI, group = SITE, LOCATION))





# 
# require(reshape2)
# 
# df.m <- melt(plot_df, LOCATION = "Label")





```
this is close to a working version but the random id(iva ave func snippet) is being assigned to values with cumulative above 1.  Don't want that.
```{r}
library(dplyr)


id_df <- c(1,1,1,1,1,2,2,2,2,2)
#var_df <- c(0,0,0,0,0)
cumulative <-  c(66,32,0,0,0,50,48,0,0,0)
#my_var <- c(100,100,100,100,100)
track_order <- c(1:10)
data.df <- data.frame(id_df,cumulative, track_order)


data.df <- data.df %>%
  group_by(id_df) %>%
  mutate(cum_sum = sum(cumulative)) %>%
  mutate(cum_minus_sum = 100-cumulative) %>%
  
  mutate(row_count = n()) %>%
  
  #generates a random id for each member of a grouping
  mutate(g_id = ave(row_count, id_df, FUN=function(x) {sample.int(length(x))})) %>%
  arrange(g_id) %>% #, .by_group = TRUE) %>%
  mutate(value = case_when(g_id <= 100 -cum_sum & cumulative <1 ~1))



```

this is the ongoing attempt to fix the issue
```{r}
library(dplyr)

#count_var <-  97

id_df <- c(1,1,1,1,1,2,2,2,2,2)
#var_df <- c(0,0,0,0,0)
cumulative <-  c(66,32,0,0,0,50,48,0,0,0)
#my_var <- c(100,100,100,100,100)
track_order <- c(1:10)
data.df <- data.frame(id_df,cumulative, track_order)


data.df <- data.df %>%
  group_by(id_df) %>%
  mutate(cum_sum = sum(cumulative)) %>%
  mutate(cum_minus_sum = 100-cumulative) %>%
  
  mutate(row_count = n()) %>%
  ungroup()

data_subset.df <- data.df %>%
  filter(cumulative == 0)
  #generates a random id for each member of a grouping
  
  #mutate(ss_test =subset(data.df$cumulative, cumulative == 0))
  
  #this part needs to apply unique ids to only the subset of the group in which cumulative  == 0, or apply
  #the unique id in a way that differentiates between cum==0 and cum!=0 in a way that makes them iterable
  mutate(g_id = ave(subset(data_subset.df$cumulative, cumulative == 0) , id_df, FUN=function(x) {sample.int(length(x))})) %>%
  arrange(g_id) %>% #, .by_group = TRUE) %>%
  mutate(value = case_when(g_id <= 100 -cum_sum & cumulative <1 ~1))

data_final.df <- left_join(data.df, data_subset.df, by= "unique_id")
  
########

```

```{r}
taxa_test.df <- taxa.df %>% 
  group_by(unique_id) %>%
  mutate(total_sum = sum(reporting_value)) %>%
  mutate(ratio = 100*(reporting_value/total_sum)) %>%
  mutate(ratio = ifelse(ratio >= 1, round(ratio), as.integer(ratio))) %>%
  mutate(cumulative = ifelse(ratio >= 1, sum(ratio), 0)) %>%
  mutate(sum_cum = ifelse(ratio >= 1, 100-cumulative, 100-(max(cumulative)))) %>%
  mutate(count = n()) %>%
```


Chessie BIBI testing code


```{r}
# taxa.df <- prob_rarefaction(taxa.df, unique_id, reporting_value, genus, 100)
```

```{r}
taxa_test.df <- taxa.df %>% 
  group_by(unique_id) %>%
  mutate(total_sum = sum(reporting_value)) %>%
  mutate(ratio = 100*(reporting_value/total_sum)) %>%
  mutate(ratio = ifelse(ratio >= 1, round(ratio), as.integer(ratio))) %>%
  mutate(cumulative = ifelse(ratio >= 1, sum(ratio), 0)) %>%
  mutate(sum_cum = ifelse(ratio >= 1, 100-cumulative, 100-(max(cumulative)))) %>%
  mutate(count = n()) %>%
  rowwise() %>%
  mutate(rc_test =(ifelse(cumulative == 0, sample(0:1, 1, replace=TRUE), ratio))) %>%
  ungroup()

taxa_test.df <- taxa_test.df %>% 
  group_by(unique_id) %>%
  mutate(rc_total = sum(rc_test)) #%>%
  # #for (n()) {
  #   for (sum_cum)}
  # #for cum_sum (mutate(elseif()))
  # summarise(rand = sample_n(.,5))
  
  #mutate(rare_count =ifelse(sum_cum != 100, sample_n(sum_cum), ratio))
```


rowwise() is a stop-gap and not a great one.  This method doesn't work because of that but even if it did it's a brute force and sloppy.
```{r}
taxa_test.df <- taxa.df %>% 
  group_by(unique_id) %>%
  mutate(total_sum = sum(reporting_value)) %>%
  mutate(ratio = 100*(reporting_value/total_sum)) %>%
  mutate(ratio = ifelse(ratio >= 1, round(ratio), as.integer(ratio))) %>%
  mutate(cumulative = ifelse(ratio >= 1, sum(ratio), 0)) %>%
  mutate(sum_cum = ifelse(ratio >= 1, 100-cumulative, 100-(max(cumulative)))) #%>%
```


```{r}
taxa_while_test.df <- taxa_test.df

while((sum(subset(taxa_while_test.df$cumulative,taxa_while_test.df$ratio <1)) / as.numeric(nrow(subset(taxa_while_test.df,taxa_while_test.df$ratio <1))))<100){

taxa_while_test.df <- taxa_while_test.df %>%
mutate(cumulative = case_when( cumulative < 100 & ratio <1 ~cumulative + 1, TRUE ~ cumulative))
}
```



```{r}
  
#   mutate(count = n()) %>%
#   rowwise() %>%
#   mutate(rc_test =(ifelse(cumulative == 0, sample(0:1, 1, replace=TRUE), ratio))) %>%
#   ungroup()
#   
# taxa_test.df <- taxa_test.df %>%
#   mutate(rc_total = sum(rc_test)) %>%
#   while (rc_total != 100) {  
#     rowwise() %>%
#     lapply(mutate(rc_test =(ifelse(cumulative == 0, sample(0:1, 1, replace=TRUE), ratio)))) %>%
#     mutate(rc_total = sum(rc_test))
#     
#   }



```

import, examine, plot, etc. netcdf data from NWM
```{r}
library(ncdf4)
library(raster)
library(sp)

project.dir <- rprojroot::find_rstudio_root_file()

ncdf_path_short <- file.path(project.dir, "data/netcdf/nwm.t00z.short_range.channel_rt.f001.conus.nc")

ncdf_path_long <- file.path(project.dir, "data/netcdf/nwm.t00z.long_range.channel_rt_1.f006.conus.nc")

ncdf_short <- nc_open(ncdf_path_short)
ncdf_long <- nc_open(ncdf_path_long)

print(ncdf_long)
```

```{r}
library(rprojroot)
library(dplyr)
library(ritis)

project.dir <- rprojroot::find_rstudio_root_file()

bay.temp <- data.table::fread(file.path(project.dir, "data/phytoplankton/", "cedr_phyto_taxa.csv")) %>%
  mutate(tsn=as.character(tsn)) %>%
  mutate(speccode = as.character(speccode)) %>%
  mutate(reportingvalue = as.integer(reportingvalue)) %>%
  mutate(samplenumber = as.character(samplenumber))

hier.wide <- lapply(unique(bay.temp$org_tsn), function(tsn.i) {
 #print(tsn.i)
  
  if(ncol(usage(tsn.i)) == 0) return(data.frame(org_tsn = as.integer(tsn.i),
                                                stringsAsFactors = FALSE))
  if(!ritis::usage(tsn.i)$taxonUsageRating %in% c("accepted", "valid")) {
    tsn.accepted <- ritis::accepted_names(as.integer(tsn.i))$acceptedTsn
  } else {
    tsn.accepted <- as.integer(tsn.i)
  }
  
  full.df <- ritis::hierarchy_full(tsn.accepted) %>% 
    select(rankname, taxonname, tsn) %>% 
    slice(1:which(tsn == tsn.accepted)) %>% 
    mutate(org_tsn = as.integer(tsn.i),
           final_tsn = as.integer(tsn.accepted),
           final_id = slice(., which(tsn == tsn.accepted))$taxonname)
}) %>% 
  bind_rows() %>% 
  select(-tsn) %>% 
  spread(rankname, taxonname) %>% 
  clean_up()
```

ritis (and lapply)
```{r}
library(rprojroot)
library(dplyr)
library(ritis)

project.dir <- rprojroot::find_rstudio_root_file()

bay.temp <- data.table::fread(file.path(project.dir, "data/CEDR/", "cedr_phyto_taxa.csv")) %>%
  mutate(tsn=as.numeric(tsn)) %>%
  mutate(speccode = as.character(speccode)) %>%
  mutate(reportingvalue = as.integer(reportingvalue)) %>%
  mutate(samplenumber = as.character(samplenumber))

accepted <- accepted_names(tsn =  504239, wt="json", raw=FALSE)

#this generates a single match, and the integer 1 is returned
count1 <- any_match_count(504239, wt="json", raw=FALSE)

#this generates zero matches, as expected, and the integer 0 is returned
count2 <- any_match_count(123123123, wt="json", raw=FALSE)

comment_detail(tsn=180543)

tsns <- c(504239,180543,2288,123)

usable <- lapply(tsns, function(tsn.i) {
  usage(tsn.i)$taxonUsageRating
  
  #thing <- ritis::common_names(tsn.i)$commonName
   }) %>% 
  bind_rows()

names <- lapply(tsns, function(tsn.i) {
  common_names(tsn.i)$commonName
  #thing <- ritis::common_names(tsn.i)$commonName
   }) %>% 
  bind_rows()

full <- lapply(tsns, function(tsn.i) {
  hierarchy_full(tsn.i)
  #thing <- ritis::common_names(tsn.i)$commonName
   }) %>% 
  bind_rows()

single_full <- hierarchy_full(2288)
# test.df <- lapply(bay.temp$tsn, function(the_func){
#   mutate(average = mean(the_func))
# })
  #test <- sum(the_func)

```

using taxize
```{r}
library(taxize)
library(ritis)

chiro_tsn <- get_tsn("Chironomus riparius")

green_tsn <- get_tsn("Chlorophyta")

blue_green_tsn <- get_tsn("Cyanobacteria")

zero_test <-  common_names("0")

test_use <- usage("956108")
test_name <- common_names("956108")

test_use2 <- usage("5414")
test_name2 <- common_names("5414")


```


exploring issue with green_cells
```{r}
green_cell_carbon.df <- missing_carbon.df %>%
  filter(latinname=="green_cells") #%>%
  #select(-size)

green_cell_tsn.df <- missing_tsn.df %>%
  filter(latinname=="green_cells") #%>%
  #select(-size)

blue_green_carbon.df <- missing_carbon.df %>%
  filter(latinname=="blue_green_sphere") #%>%
  #select(-size)

blue_green_tsn.df <- missing_tsn.df %>%
  filter(latinname=="blue_green_sphere") #%>%



blue_green_sphere.df <- bay_merged.df %>%
  filter(latinname %in% c("blue_green_sphere","green_cells"))

blue_green_sphere_carbon.df <- carbon.df %>%
  filter(latinname %in% c("green_cells","blue_green_sphere"))

blue_green_sphere_carbon.df <- left_join(blue_green_sphere.df, carbon.df, by= c("latinname","size"))

# bay_w_size.df <- bay_partials_added.df %>%
#   #filter(size != as.character(NA))
#   filter(!size == "not_applicable")


green.df <- left_join(green_cell.df, carbon.df, by= c("latinname"))

chiro <- bay_merged.df %>% filter(latinname %in% c("chironomus_riparius"))

```

no tsn blue_green_sphere but there is tsn for Cyanobacteria.  can this be used instead?  Aslo, check for an alias for green_cells as well.
```{r}
# green_tsn <- get_tsn("Cyanobacteria")
# 
# test <- usage("956108")
# test <- common_names("956108")
# 
# test <- phyto.df %>%
# filter(latinname%in% c("chironomus_riparius","chlorophyta","cryptomonas","green_cells"))
# 
# print(missing_tsn_names <- unique(missing_tsn.df$latinname))
# 
# print(missingcarbon_names <- unique(missing_carbon.df$latinname))
```

```{r}
# c( "green_cells","blue_green_sphere","cylindrospermopsis","woronichinia_naegeliana","limnothrix"            ,"protoperidinium_orbiculare")


```

```{r}
num <- "003402"
nums_fixed <- gsub("(^|[^0-9])0+", "\\1", as.integer(num), perl = TRUE)
```

for Andrea 
```{r}
library(MBSStools)
library(dplyr)

myIndex <- "MBSS.2005.Bugs"

thresh <- MBSStools::metrics_scoring

myMetrics.Bugs.MBSS <- as.character(droplevels(unique(thresh[thresh[,"Index.Name"]==myIndex, "MetricName"])))


testMetric <-  as.character(droplevels(unique(thresh[test, "MetricName"])))
test1 <- #unique(
  thresh[thresh[,"Index.Name"]==myIndex, "Metrics"]#)

test <- thresh[,"Index.Name"]==myIndex
print(typeof(test))
print(test)

```

```{r}
library(readxl)
library(dplyr)


#creates project.dir, phyto directory object 
project.dir <- rprojroot::find_rstudio_root_file()

reservoir.df <- read_excel(file.path(project.dir, "data/Reservoir_Intake_test.xlsx"),
                         sheet = "NorbData"#,
                         #skip = 1
                         )

reservoir.df <-  reservoir.df %>%
  mutate(Id = paste0(Year,Mon)) 

#move last column (id) to first
reservoir.df<-reservoir.df[,c(29, 1:28)]

reservoir.df %>%  
data.table::fwrite(file.path(project.dir, "data/", "Reservoir_intake.csv"))

reservoir.df %>%  
data.table::fwrite(file.path(project.dir, "data/", "Reservoir_intake.xlsx"))

test.df <- reservoir.df %>%
  select(Id, Year, Mon, Res)

test.df %>%  
data.table::fwrite(file.path(project.dir, "data/", "Test.xlsx"))

test.df %>%  
data.table::fwrite(file.path(project.dir, "data/", "Test.csv"))


```