---
title: "Phyto_Shiny"
author: "Luke Vawter"
date: "August 29, 2018"
output: html_document
---

This is a place for general notes as I examine, unpack, and eventually come to understand Zach's R/Shiny code for the Phyto project.

I'm using this process as a way to:
1) learning R markdown
2) improve my understanding of Zach's code
3) practice comprehensive documentation
4) document so I can repeat and others can follow

Directory structure is important for maintainability/ scalability of code.  The three main components of a Shiny app are global, ui and server (making up initial directory branching).  Shiny looks for directories with these names for use.

The current task for the Phyto project is to resolve appendix output.  Current outputs are incorrect.

Below I will play with some R code, included in the Phyto appendix code, that was unfamiliar to me:

```{r}
##this uses a case when structure from dplyr to replicate the structure of an if else control flow structure
library("dplyr")
x <- 26
case_when(x > 25 ~ "big",
          x > 15 ~ "medium",
          x > 5 ~ "small")
```
```{r}
##playing with the mutate
library("dplyr")
name <- c("tom","jerry")
start_age <- c(12,13)
years_in <- c(3,2)

test.df <- data.frame(name,age
  
)
test.df %>%
  mutate(current_age  = start_age + years_in)

print(test.df)
```

