---
title: "Chessie BIBI Rating Verification"
date: <h4 style="font-style:normal">`r format(Sys.time(), '%d %B, %Y')`</h4>
author:
  - name: "Rikke D. Jepsen, rjepsen@icprb.org"
    affiliation: Interstate Commission on the Potomac River Basin
output:
  html_document:
    df_print: paged
    toc: true
    toc_float: true
---
```{r setup, cache = F, echo = F}
 knitr::opts_chunk$set(error = TRUE)
```
### **Introduction**
Taxa richness and diversity metrics for a stream macroinvertebrate sample are influenced by the total number of organisms in the sample. Higher total counts make it more likely to find rarer species in the sample. In order to compare richness and diversity across all samples, the R-program for calculating the Chessie BIBI index performs a probabilistic rarefaction and normalizes all sample counts to 100 organisms. The probabilistic rarefaction steps are described in Smith et al. (2017) page 7 and Appendix D and implemented in Step 1.5 of the Chessie BIBI program. As warned in the report and program documentation, the normalized sample created by the probabilistic rarefaction step is slightly different each time the program is run. This is because it randomly selects the rarer taxa to include in the BIBI calculation. If the program randomly selects a rare taxon that belongs to a commonly found family, Taxa Richness is unaffected because all genera are rolled-up to family level for the family-level, bioregion-specific Chessie BIBI index. If the program randomly picks a rare taxon that belongs to a rarely found family, the calculated richness and diversity metrics are higher. Richness and diversity are sensitive to disturbance and one or more of them are included in all of the twelve bioregion-specific indexes (see Table 15 in Smith et al. 2017). A difference of one or two families in the count of a sample’s families can change the final BIBI score and sometimes its rating.    

We have developed a program that will remove some of the uncertainty by determining which index rating (Excellent, Good, Fair, Poor, or Very Poor) has the highest probability of being the correct rating from repeated runs of the Chessie BIBI program.

### **1.Setup**
####**1.1 Data import**
Import the rarefied and non-rarefied data frames that were exported from the first run of the Chessie BIBI program, **taxa.df** and **taxa.df4**, respectively. 
```{r}
#setwd("C:/Users/RJepson/OneDrive - ICPRB/Refining Chessie BIBI/Rerunning metrics on cleaned data")
setwd("C:/Users/lcvaw/OneDrive/Documents/R/workflow/Chessie_bibi/problem_4_30_2020")
# Non-rarefied dataset
taxa.df <- read.csv("taxa.df.csv") 

# Rarefied dataset
taxa.df4 <- read.csv("taxa.df4.csv")
```
#### **1.2 Package loading**
Load the *tidyverse* and *benthos* packages. 
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(benthos)
```
### **2. Function creation**  
Create a function that will let you repeat the Chessie BIBI program a set number of times.
```{r message=FALSE, warning=FALSE}
   
ChessieBIBI_score <- function(){
      # Rarefaction
      taxa2.df <- taxa.df %>%                                                                      
        group_by(unique_id) %>%                                                                               
        mutate(sample_sum = sum(reporting_value)) %>%                                                         
        mutate(ratio = 100*(reporting_value/sample_sum)) %>%                                                  
        mutate(ratio_int = ifelse(ratio >= 1, round(ratio), as.integer(ratio))) %>%                           
        mutate(cumulative = ifelse(ratio_int >= 1, sum(ratio_int), 0)) %>%                                    
        mutate(rare_needed = as.integer(ifelse(ratio_int >= 1, 100-cumulative, 100-(max(cumulative))))) %>%   
        mutate(count= n()) %>%
        mutate(random = sample(100, size = n(), replace = FALSE)) %>%                                         
        arrange(ratio_int, random) %>%                                                                        
        ungroup()                                                                                             
       
       taxa3.df <- taxa2.df %>%
         group_by(unique_id) %>%
         mutate(rare_num = case_when(ratio_int == 0 ~ TRUE, ratio_int != 0 ~ FALSE)) %>%                      
         summarise(total_rare = sum(rare_num)) %>%                                                            
         ungroup()
       
       taxa_join <- left_join(taxa2.df, taxa3.df, by = "unique_id") %>%                            
         group_by(unique_id) %>%
         mutate(rare_needed = ifelse(rare_needed > total_rare, total_rare, rare_needed)) %>%                   
         mutate(rare_needed = ifelse(rare_needed < 1, 0, rare_needed)) %>%                                   
         mutate(rare_2b_removed = (total_rare - rare_needed)+1) %>%                                          
         slice(median(rare_2b_removed):n()) %>%                                                                       
         mutate(rare_count =(ifelse(ratio_int == 0, 1, ratio_int))) %>%                                       
         mutate(rare_count_total = sum(rare_count)) %>%                                                        
         ungroup()
         
       taxa.df4 <- taxa_join %>%                                                                               
        select(unique_id, icprb_bioregion_id, rare_count, phylum, subphylum, class, subclass, order, suborder, family, subfamily, tribe, genus, habit, species, ffg, bibi_tv)
      
       # Create a data frame of the non-rarefied and rarefied data.
      non_rare <- taxa.df %>%
      arrange(unique_id) %>%
      ungroup()

      rare <- taxa.df4 %>%
      arrange(unique_id) %>%
      ungroup()

# Create the metrics.key data frame.
metrics.key <- taxa.df %>%              
 select(unique_id, icprb_bioregion_id, station_id, sample_date, sample_time) %>%
 unique() %>%
 arrange(unique_id) 

# ESTABLISH FUNCTIONS USED TO CALCULATE SOME METRICS
###--------------------------------------------------------------------------
original_order <- function(mod.df, original.df, unique.id.col) {
  unique.id.col <- rlang::enquo(unique.id.col)

  final.df <- original.df %>%
    dplyr::select(!!unique.id.col) %>%
    dplyr::distinct() %>%
    dplyr::left_join(mod.df, by = rlang::quo_name(unique.id.col))

  return(final.df)
}
###--------------------------------------------------------------------------
## CALCULATE THE METRICS ##
# Calculate how many individuals are in each unique_id (unique sampling event)
sample_sum <- non_rare %>%
 group_by(unique_id) %>%
 summarise(sample_sum = sum(reporting_value)) 

#
 aspt_mod <- function(long.df, unique.id.col, count.col, tol.col) {
  unique.id.col <- rlang::enquo(unique.id.col)
  tol.col <- rlang::enquo(tol.col )
  count.col <- rlang::enquo(count.col )
  #----------------------------------------------------------------------------
  long.df <- long.df %>%
    dplyr::filter((!!count.col) > 0)
  #----------------------------------------------------------------------------
 score.vec <- long.df %>%
    filter(!is.na(!!!tol.col),
           !rlang::UQ(tol.col) %in% c("")) %>%
    select(!!unique.id.col, !!tol.col, !!count.col) %>%
    mutate(score = rlang::UQ(count.col) * rlang::UQ(tol.col)) %>%
    group_by(!!unique.id.col) %>%
    summarize(score = sum(score),
              taxa = sum(!!count.col),
              score = score / taxa) %>%
    original_order(long.df, !!unique.id.col) %>%
    pull(score)

  return(score.vec)
}

metrics.key$aspt_mod <- aspt_mod(non_rare, unique_id, reporting_value, aspt) 

# pct_gastro_oligo 
pct_gastro_oligo <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(class)) %>% 
 summarise(sum = sum(reporting_value[class %in% c("gastropoda", "oligochaeta")]))  
 metrics.key$pct_gastro_oligo <- (pct_gastro_oligo$sum / sample_sum$sample_sum )*100

# pct_diptera
pct_diptera <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("diptera")]))  
 metrics.key$pct_diptera <- (pct_diptera$sum / sample_sum$sample_sum)*100

# GOLD  
metrics.key$gold <- 100 - (metrics.key$pct_gastro_oligo + metrics.key$pct_diptera) 

# HBI    
hbi_multiplier <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>% 
 summarise(multiplier = sum(reporting_value*bibi_tv)) 

hbi_divisor <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>% 
 summarise(divisor = sum(reporting_value))

metrics.key$hbi <- hbi_multiplier$multiplier / hbi_divisor$divisor

# pct_arthropoda      
pct_arthropoda <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(phylum)) %>% 
 summarise(sum = sum(reporting_value[phylum %in% c("arthropoda")]))  
 metrics.key$pct_arthropoda <- (pct_arthropoda$sum / sample_sum$sample_sum )*100

# pct_burrow    
pct_burrow <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>% 
 summarise(sum = sum(reporting_value[habit %in% c("burrow")]))  
 metrics.key$pct_burrow <- (pct_burrow$sum / sample_sum$sample_sum )*100
 
# pct_chironomidae   
pct_chironomidae <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(family)) %>% 
 summarise(sum = sum(reporting_value[family %in% c("chironomidae")]))  
 metrics.key$pct_chironomidae <- (pct_chironomidae$sum / sample_sum$sample_sum )*100

# pct_cling  
pct_cling <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>% 
 summarise(sum = sum(reporting_value[habit %in% c("cling")]))  
 metrics.key$pct_cling <- (pct_cling$sum / sample_sum$sample_sum )*100  

#pct_collect 
pct_collect <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>% 
 summarise(sum = sum(reporting_value[ffg %in% c("filter", "gather")]))  
 metrics.key$pct_collect <- (pct_collect$sum / sample_sum$sample_sum )*100    

# pct_cote    
pct_cote <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("coleoptera", "trichoptera", "ephemeroptera", "odonata")]))  
 metrics.key$pct_cote <- (pct_cote$sum / sample_sum$sample_sum )*100

# pct_ephemeroptera    
pct_ephemeroptera <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("ephemeroptera")]))  
 metrics.key$pct_ephemeroptera <- (pct_ephemeroptera$sum / sample_sum$sample_sum )*100

# pct_baetidae    
pct_baetidae <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(family)) %>% 
 summarise(sum = sum(reporting_value[family %in% c("baetidae")]))  
 metrics.key$pct_baetidae <- (pct_baetidae$sum / sample_sum$sample_sum )*100
 
# pct_ephemeroptera_no_baetid       
pct_ephemeroptera_no_baetid <- pct_baetidae
pct_ephemeroptera_no_baetid$sum_ephemeroptera <- pct_ephemeroptera$sum 
pct_ephemeroptera_no_baetid$ephem_no_baetidae <- pct_ephemeroptera_no_baetid$sum_ephemeroptera - pct_ephemeroptera_no_baetid$sum
metrics.key$pct_ephemeroptera_no_baetid <- (pct_ephemeroptera_no_baetid$ephem_no_baetidae/sample_sum$sample_sum)*100

# pct_ept  
pct_ept <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("ephemeroptera", "plecoptera", "trichoptera")]))  
 metrics.key$pct_ept <- (pct_ept$sum / sample_sum$sample_sum )*100
  
# pct_hydropsychidae    
pct_hydropsychidae <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(family)) %>% 
 summarise(sum = sum(reporting_value[family %in% c("hydropsychidae")]))  
 metrics.key$pct_hydropsychidae <- (pct_hydropsychidae$sum / sample_sum$sample_sum )*100

# pct_ept_no_hydro    
pct_ept_hydro <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[family %in% c("hydropsychidae")]))
 pct_ept_hydro$subtract <- pct_ept$sum - pct_ept_hydro$sum
 metrics.key$pct_ept_no_hydro <- (pct_ept_hydro$subtract/pct_ept$sum)*100

# pct_euholognatha  
pct_euholognatha <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(suborder)) %>% 
 summarise(sum = sum(reporting_value[suborder %in% c("euholognatha")]))
 metrics.key$pct_euholognatha <- (pct_euholognatha$sum / sample_sum$sample_sum )*100
  
# pct_filter    
pct_filter <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>% 
 summarise(sum = sum(reporting_value[ffg %in% c("filter")]))  
 metrics.key$pct_filter <- (pct_filter$sum / sample_sum$sample_sum )*100

# pct_heptageniidae    
pct_heptageniidae <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(family)) %>% 
 summarise(sum = sum(reporting_value[family %in% c("heptageniidae")]))  
 metrics.key$pct_heptageniidae <- (pct_heptageniidae$sum / sample_sum$sample_sum )*100

# pct_hexapoda    
pct_hexapoda <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(subphylum)) %>% 
 summarise(sum = sum(reporting_value[subphylum %in% c("hexapoda")]))  
 metrics.key$pct_hexapoda <- (pct_hexapoda$sum / sample_sum$sample_sum )*100

# pct_hydro_ept    
metrics.key$pct_hydro_ept <- ifelse(metrics.key$pct_ept == 0, 0, (metrics.key$pct_hydropsychidae / metrics.key$pct_ept) * 100)

# pct_intol_0_3    
pct_intol_0_3 <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>% 
 summarise(sum = sum(reporting_value[bibi_tv %in% c("0", "1", "2", "3")]))  
 metrics.key$pct_intol_0_3 <- (pct_intol_0_3$sum / sample_sum$sample_sum)*100
  
# pct_intol_0_4   
pct_intol_0_4 <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>% 
 summarise(sum = sum(reporting_value[bibi_tv %in% c("0", "1", "2", "3", "4")]))  
 metrics.key$pct_intol_0_4 <- (pct_intol_0_4$sum / sample_sum$sample_sum)*100

# pct_amph_iso  
pct_amph_iso <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("amphipoda", "isopoda")]))  
 metrics.key$pct_amph_iso <- (pct_amph_iso$sum / sample_sum$sample_sum )*100  

# pct_ephemerellidae  
pct_ephemerellidae <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(family)) %>% 
 summarise(sum = sum(reporting_value[family %in% c("ephemerellidae")]))  
 metrics.key$pct_ephemerellidae <- (pct_ephemerellidae$sum / sample_sum$sample_sum )*100  

# pct_limestone    
metrics.key$pct_limestone <- metrics.key$pct_amph_iso + metrics.key$pct_ephemerellidae

# pct_mod_tol_4_6 
pct_mod_tol_4_6 <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>% 
 summarise(sum = sum(reporting_value[bibi_tv %in% c("4", "5", "6")]))  
 metrics.key$pct_mod_tol_4_6 <- (pct_mod_tol_4_6$sum / sample_sum$sample_sum)*100  

# pct_trichoptera    
pct_trichoptera <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("trichoptera")]))  
 metrics.key$pct_trichoptera <- (pct_trichoptera$sum / sample_sum$sample_sum )*100  

# pct_non_hydrop_trichoptera  
pct_non_hydrop_trichoptera <- pct_trichoptera
pct_non_hydrop_trichoptera$hydropsychidae <- pct_hydropsychidae$sum
pct_non_hydrop_trichoptera$subtract <- pct_non_hydrop_trichoptera$sum - pct_non_hydrop_trichoptera$hydropsychidae
metrics.key$pct_non_hydrop_trichoptera <- (pct_non_hydrop_trichoptera$subtract/pct_non_hydrop_trichoptera$sum)*100

# pct_odonata  
pct_odonata <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>% 
 summarise(sum = sum(reporting_value[order %in% c("odonata")]))  
 metrics.key$pct_odonata <- (pct_odonata$sum / sample_sum$sample_sum )*100  
  
# pct_pisciforma  
pct_pisciforma <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(suborder)) %>% 
 summarise(sum = sum(reporting_value[suborder %in% c("pisciforma")]))  
 metrics.key$pct_pisciforma <- (pct_pisciforma$sum / sample_sum$sample_sum )*100  

# pct_predator  
pct_predator <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>% 
 summarise(sum = sum(reporting_value[ffg %in% c("predator")]))  
 metrics.key$pct_predator <- (pct_predator$sum / sample_sum$sample_sum )*100  
  
# pct_pterygota  
pct_pterygota <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(subclass)) %>% 
 summarise(sum = sum(reporting_value[subclass %in% c("pterygota")]))  
 metrics.key$pct_pterygota <- (pct_pterygota$sum / sample_sum$sample_sum )*100 

# pct_retreat_caddisfly  
pct_retreat_caddisfly <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(suborder)) %>% 
 summarise(sum = sum(reporting_value[suborder %in% c("annulipalpia")]))  
 metrics.key$pct_retreat_caddisfly <- (pct_retreat_caddisfly$sum / sample_sum$sample_sum )*100 

# pct_scrape   
pct_scrape <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>% 
 summarise(sum = sum(reporting_value[ffg %in% c("scrape")]))  
 metrics.key$pct_scrape <- (pct_scrape$sum / sample_sum$sample_sum )*100 
   
# pct_sprawl   
pct_sprawl <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>% 
 summarise(sum = sum(reporting_value[habit %in% c("sprawl")]))  
 metrics.key$pct_sprawl <- (pct_sprawl$sum / sample_sum$sample_sum )*100 

# pct_systellognatha   
pct_systellognatha <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(suborder)) %>% 
 summarise(sum = sum(reporting_value[suborder %in% c("systellognatha")]))  
 metrics.key$pct_systellognatha <- (pct_systellognatha$sum / sample_sum$sample_sum )*100 

# pct_tolerant_7_10   
pct_tolerant_7_10 <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>% 
 summarise(sum = sum(reporting_value[bibi_tv %in% c("7", "8", "9", "10")]))  
 metrics.key$pct_tolerant_7_10 <- (pct_tolerant_7_10$sum / sample_sum$sample_sum)*100 

# pct_urban_intol   
pct_urban_intol <- non_rare %>%
 group_by(unique_id) %>%
 filter(!is.na(family)) %>% 
 summarise(sum = sum(reporting_value[family %in% c(
    "aeshnidae",
    "ameletidae",
    "asellidae",
    "athericidae",
    "baetidae",
    "brachycentridae",
    "caenidae",
    "calamoceratidae",
    "cambaridae",
    "capniidae",
    "ceratopogonidae",
    "chironomidae",
    "chloroperlidae",
    "cordulegastridae",
    "corduliidae",
    "corydalidae",
    "crangonyctidae",
    "elmidae",
    "ephemerellidae",
    "ephemeridae",
    "glossosomatidae",
    "gomphidae",
    "heptageniidae",
    "hydropsychidae",
    "hydroptilidae",
    "isonychiidae",
    "lepidostomatidae",
    "leptophlebiidae",
    "leuctridae",
    "libellulidae",
    "metretopodidae",
    "nemouridae",
    "odontoceridae",
    "peltoperlidae",
    "perlidae",
    "perlodidae",
    "philopotamidae",
    "phryganeidae",
    "polycentropodidae",
    "polymitarcyidae",
    "potamanthidae",
    "psephenidae",
    "pteronarcyidae",
    "rhyacophilidae",
    "sericostomatidae",
    "sialidae",
    "simuliidae",
    "stratiomyidae",
    "tabanidae",
    "taeniopterygidae",
    "tipulidae",
    "uenoidae",
    "viviparidae")]))  
  metrics.key$pct_urban_intol <- (pct_urban_intol$sum / sample_sum$sample_sum )*100 

# Richness and diversity metrics require rarefied data
# Calculate family-level taxa richness for each unique_id
family_richness <- rare %>%
 group_by(unique_id) %>%
 summarise(family_richness = n_distinct(family)) 

# Margalefs
margalefs_numerator <- family_richness %>%
 mutate(family_richness = family_richness - 1)

margalefs_denominator <- rare %>%
 group_by(unique_id) %>%
 summarise(sample_sum = log(sum(rare_count)))

metrics.key$margalefs <- margalefs_numerator$family_richness / margalefs_denominator$sample_sum

# pct_ept_rich
pct_ept_rich <- rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>%
 filter(order %in% c("ephemeroptera", "plecoptera", "trichoptera")) %>%
 summarise(rich_ept = n_distinct(family))
 pct_ept_rich2 <- merge(pct_ept_rich, family_richness, by= "unique_id", all=TRUE)
 pct_ept_rich2[is.na(pct_ept_rich2)] <- 0
 metrics.key$pct_ept_rich <- (pct_ept_rich2$rich_ept / pct_ept_rich2$family_richness)*100
    
# pct_ept_rich_no_tol    
pct_ept_rich_no_tol <- rare %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>%
 filter(order %in% c("ephemeroptera", "plecoptera", "trichoptera")) %>%
 filter(bibi_tv %in% c("0","1","2","3","4","5","6")) %>%
 summarise(rich_ept_no_tol = n_distinct(family))
 pct_ept_rich_no_tol2 <- merge(pct_ept_rich_no_tol, family_richness, by= "unique_id", all=TRUE)
 pct_ept_rich_no_tol2[is.na(pct_ept_rich_no_tol2)] <- 0
 metrics.key$pct_ept_rich_no_tol <- (pct_ept_rich_no_tol2$rich_ept_no_tol / pct_ept_rich_no_tol2$family_richness)*100  

# Pielou
pielou_shannon <- rare %>%
 group_by(unique_id) %>%
 summarise(shannon = shannon(taxon = family, count= rare_count))

pielou_taxa_rich <- family_richness %>%
  group_by(unique_id) %>%
  mutate(family_richness = log2(family_richness))

metrics.key$pielou <- pielou_shannon$shannon / pielou_taxa_rich$family_richness

# rich_burrow  
rich_burrow <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>%
 filter(habit %in% c("burrow")) %>%
 summarise(rich_burrow = n_distinct(family)) %>%
 select(unique_id, rich_burrow) 
 metrics.key <- merge(metrics.key, rich_burrow, by="unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 
  
# rich_climb
rich_climb <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>%
 filter(habit %in% c("climb")) %>%
 summarise(rich_climb = n_distinct(family)) %>%
 select(unique_id, rich_climb) 
 metrics.key <- merge(metrics.key, rich_climb, by="unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 
  
# rich_cling 
rich_cling <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>%
 filter(habit %in% c("cling")) %>%
 summarise(rich_cling = n_distinct(family)) %>%
 select(unique_id, rich_cling) 
 metrics.key <- merge(metrics.key, rich_cling, by="unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 
 
# rich_collect   
rich_collect_filter <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>%
 filter(ffg %in% c("filter")) %>%
 summarise(rich_collect_filter = n_distinct(family)) %>%
 select(unique_id, rich_collect_filter)
 
rich_collect_gather <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>%
 filter(ffg %in% c("gather")) %>%
 summarise(rich_collect_gather = n_distinct(family)) %>%
 select(unique_id, rich_collect_gather)
 rich_collect <- merge(rich_collect_filter, rich_collect_gather, by = "unique_id", all=TRUE)
 rich_collect[is.na(rich_collect)] <- 0  
 rich_collect$rich_collect <- rich_collect$rich_collect_filter + rich_collect$rich_collect_gather
 rich_collect$rich_collect_gather <- NULL
 rich_collect$rich_collect_filter <- NULL
 metrics.key <- merge(metrics.key, rich_collect, by = "unique_id", all=TRUE)
   
# rich_ephemeroptera     
rich_ephemeroptera <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>%
 filter(order %in% c("ephemeroptera")) %>%
 summarise(rich_ephemeroptera = n_distinct(family)) %>%
 select(unique_id, rich_ephemeroptera) 
 metrics.key <- merge(metrics.key, rich_ephemeroptera, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0
     
# rich_ept    
rich_ept <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>%
 filter(order %in% c("ephemeroptera", "plecoptera", "trichoptera")) %>%
 summarise(rich_ept = n_distinct(family)) %>%
 select(unique_id, rich_ept) 
 metrics.key <- merge(metrics.key, rich_ept, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0   
 
# rich_filter    
rich_filter <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>%
 filter(ffg %in% c("filter")) %>%
 summarise(rich_filter = n_distinct(family)) %>%
 select(unique_id, rich_filter) 
 metrics.key <- merge(metrics.key, rich_filter, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0   

# rich_gather    
rich_gather <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>%
 filter(ffg %in% c("gather")) %>%
 summarise(rich_gather = n_distinct(family)) %>%
 select(unique_id, rich_gather) 
 metrics.key <- merge(metrics.key, rich_gather, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0   

# rich_intol 
rich_intol0 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("0")) %>%
 summarise(rich_intol0 = n_distinct(family)) %>%
 select(unique_id, rich_intol0)

rich_intol1 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("1")) %>%
 summarise(rich_intol1 = n_distinct(family)) %>%
 select(unique_id, rich_intol1)

rich_intol2 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("2")) %>%
 summarise(rich_intol2 = n_distinct(family)) %>%
 select(unique_id, rich_intol2)

rich_intol3 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("3")) %>%
 summarise(rich_intol3 = n_distinct(family)) %>%
 select(unique_id, rich_intol3)
 rich_intol01 <- merge(rich_intol0, rich_intol1, by= "unique_id", all=TRUE)
 rich_intol01[is.na(rich_intol01)] <- 0
 rich_intol012 <- merge(rich_intol01, rich_intol2, by= "unique_id", all=TRUE)
 rich_intol012[is.na(rich_intol012)] <- 0
 rich_intol0123 <- merge(rich_intol012, rich_intol3, by= "unique_id", all=TRUE)
 rich_intol0123[is.na(rich_intol0123)] <- 0
 rich_intol0123$rich_intol <- rich_intol0123$rich_intol0 + rich_intol0123$rich_intol1 + rich_intol0123$rich_intol2 + rich_intol0123$rich_intol3
 
rich_intol0123 <- rich_intol0123 %>%
 select(unique_id, rich_intol)
 metrics.key <- merge(metrics.key, rich_intol0123, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0   

# rich_modtol  
rich_modtol4 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("4")) %>%
 summarise(rich_modtol4 = n_distinct(family)) %>%
 select(unique_id, rich_modtol4)

rich_modtol5 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("5")) %>%
 summarise(rich_modtol5 = n_distinct(family)) %>%
 select(unique_id, rich_modtol5)

rich_modtol6 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("6")) %>%
 summarise(rich_modtol6 = n_distinct(family)) %>%
 select(unique_id, rich_modtol6)
 rich_modtol45 <- merge(rich_modtol4, rich_modtol5, by= "unique_id", all=TRUE)
 rich_modtol45[is.na(rich_modtol45)] <- 0
 rich_modtol456 <- merge(rich_modtol45, rich_modtol6, by= "unique_id", all=TRUE)
 rich_modtol456[is.na(rich_modtol456)] <- 0
 rich_modtol456$rich_modtol <- rich_modtol456$rich_modtol4 + rich_modtol456$rich_modtol5 + rich_modtol456$rich_modtol6
 
 rich_modtol456 <- rich_modtol456 %>%
 select(unique_id, rich_modtol)
 metrics.key <- merge(metrics.key, rich_modtol456, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0  
  
# rich_plecoptera  
rich_plecoptera <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>%
 filter(order %in% c("plecoptera")) %>%
 summarise(rich_plecoptera = n_distinct(family)) %>%
 select(unique_id, rich_plecoptera) 
 metrics.key <- merge(metrics.key, rich_plecoptera, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0  

# rich_predator    
rich_predator <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>%
 filter(ffg %in% c("predator")) %>%
 summarise(rich_predator = n_distinct(family)) %>%
 select(unique_id, rich_predator) 
 metrics.key <- merge(metrics.key, rich_predator, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 
 
# rich_shred    
rich_shred <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(ffg)) %>%
 filter(ffg %in% c("shred")) %>%
 summarise(rich_shred = n_distinct(family)) %>%
 select(unique_id, rich_shred) 
 metrics.key <- merge(metrics.key, rich_shred, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 

# rich_sprawl    
rich_sprawl <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(habit)) %>%
 filter(habit %in% c("sprawl")) %>%
 summarise(rich_sprawl = n_distinct(family)) %>%
 select(unique_id, rich_sprawl) 
 metrics.key <- merge(metrics.key, rich_sprawl, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 
    
# rich_tol    
rich_tol7 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("7")) %>%
 summarise(rich_tol7 = n_distinct(family)) %>%
 select(unique_id, rich_tol7)

rich_tol8 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("8")) %>%
 summarise(rich_tol8 = n_distinct(family)) %>%
 select(unique_id, rich_tol8)

rich_tol9 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("9")) %>%
 summarise(rich_tol9 = n_distinct(family)) %>%
 select(unique_id, rich_tol9)

rich_tol10 <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(bibi_tv)) %>%
 filter(bibi_tv %in% c("10")) %>%
 summarise(rich_tol10 = n_distinct(family)) %>%
 select(unique_id, rich_tol10)
 rich_tol78 <- merge(rich_tol7, rich_tol8, by= "unique_id", all=TRUE)
 rich_tol78[is.na(rich_tol78)] <- 0
 rich_tol789 <- merge(rich_tol78, rich_tol9, by= "unique_id", all=TRUE)
 rich_tol789[is.na(rich_tol789)] <- 0
 rich_tol78910 <- merge(rich_tol789, rich_tol10, by= "unique_id", all=TRUE)
 rich_tol78910[is.na(rich_tol78910)] <- 0
 rich_tol78910$rich_tol <- rich_tol78910$rich_tol7 + rich_tol78910$rich_tol8 + rich_tol78910$rich_tol9 + rich_tol78910$rich_tol10
 
rich_tol78910 <- rich_tol78910 %>%
 select(unique_id, rich_tol)
 metrics.key <- merge(metrics.key, rich_tol78910, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0   
    
# rich_trichoptera  
rich_trichoptera <- rare  %>%
 group_by(unique_id) %>%
 filter(!is.na(order)) %>%
 filter(order %in% c("trichoptera")) %>%
 summarise(rich_trichoptera = n_distinct(family)) %>%
 select(unique_id, rich_trichoptera) 
 metrics.key <- merge(metrics.key, rich_trichoptera, by = "unique_id", all=TRUE)
 metrics.key[is.na(metrics.key)] <- 0 
      
# Split unique_id into its constituent parts (event_id and sample_num)
metrics.key <- metrics.key %>%
  separate(unique_id, c('event_id', 'sample_num'), sep="_", remove = FALSE)
 
# Subset data by bioregion
NAPU <- metrics.key %>% filter(icprb_bioregion_id == "napu")
NCA <- metrics.key %>% filter(icprb_bioregion_id == "nca")
CA <- metrics.key %>% filter(icprb_bioregion_id == "ca")
MAC<- metrics.key %>% filter(icprb_bioregion_id == "mac")
SEP <- metrics.key %>% filter(icprb_bioregion_id == "sep")
BLUE <- metrics.key %>% filter(icprb_bioregion_id == "blue")
NRV <- metrics.key %>% filter(icprb_bioregion_id == "nrv")
SRV <- metrics.key %>% filter(icprb_bioregion_id == "srv")
UNP <- metrics.key %>% filter(icprb_bioregion_id == "unp")
SGV <- metrics.key %>% filter(icprb_bioregion_id == "sgv")
LNP <- metrics.key %>% filter(icprb_bioregion_id == "lnp")
PIED <- metrics.key %>% filter(icprb_bioregion_id == "pied")

#Select metrics for each bioregion
#Northern Appalachian Plateau and Uplands (NAPU)
NAPU_score <- NAPU %>% 
  select(
  "unique_id",
  "event_id",
  "sample_num",
  "icprb_bioregion_id",
  "station_id",
  "sample_date",
  "sample_time",
  "margalefs", 
  "pct_cling",
  "pct_collect",
  "pct_ephemeroptera",
  "pct_ept",
  "pct_ept_no_hydro",
  "pct_ept_rich_no_tol",
  "pct_filter",
  "pct_intol_0_3",
  "pct_non_hydrop_trichoptera",
  "pct_scrape",
  "pielou",
  "rich_burrow",
  "rich_cling",
  "rich_gather",
  "rich_modtol",
  "rich_plecoptera",
  "rich_shred",
  "rich_sprawl")
       
# North Central Appalachians (NCA)
NCA_score <- NCA %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "pct_cote",
    "pct_ephemeroptera",
    "pct_heptageniidae",
    "pct_limestone",
    "rich_cling",
    "rich_ephemeroptera",
    "rich_ept",
    "rich_plecoptera")

# Central Appalachians (CA)
CA_score <- CA %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "pct_ept_rich",
    "pct_euholognatha",
    "pct_heptageniidae",
    "pct_hydro_ept",
    "pct_mod_tol_4_6",
    "pct_non_hydrop_trichoptera",
    "pct_pisciforma",
    "pct_systellognatha",
    "rich_burrow",
    "rich_collect",
    "rich_filter",
    "rich_plecoptera",
    "rich_predator")

# Middle Atlantic Coastal Plain (MAC)
MAC_score <- MAC %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "gold",
    "pct_arthropoda",
    "pct_chironomidae",
    "pct_collect",
    "pct_mod_tol_4_6",
    "pct_odonata",
    "pct_predator",
    "pct_scrape",
    "pct_urban_intol",
    "rich_climb",
    "rich_tol")

# Southeastern Plains (SEP)
SEP_score <- SEP %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "gold",
    "hbi",
    "pct_cling",
    "pct_cote",
    "pct_ept_rich_no_tol",
    "rich_cling",
    "rich_collect",
    "rich_ephemeroptera",
    "rich_filter",
    "rich_trichoptera")

# Blue Ridge (BLUE)
BLUE_score <- BLUE %>% 
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "pct_burrow",
    "pct_ept_rich_no_tol",
    "pct_scrape",
    "pct_systellognatha",
    "rich_ephemeroptera")

# Northern Ridge and Valley (NRV)
NRV_score <- NRV %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "pct_ephemeroptera_no_baetid",
    "pct_ept_rich",
    "rich_collect",
    "rich_ephemeroptera",
    "rich_predator",
    "rich_shred",
    "rich_trichoptera")

# Southern Ridge and Valley (SRV)
SRV_score <- SRV %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "pct_burrow",
    "pct_cling",
    "pct_cote",
    "pct_ephemeroptera_no_baetid",
    "pct_ept_rich_no_tol",
    "pct_predator",
    "pct_scrape",
    "rich_cling",
    "rich_collect",
    "rich_ephemeroptera",
    "rich_intol",
    "rich_plecoptera",
    "rich_predator",
    "rich_trichoptera")

# Upper Northern Piedmont (UNP)
UNP_score <- UNP %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "hbi",
    "pct_collect",
    "pct_ept_rich_no_tol",
    "pct_filter",
    "pct_hexapoda",
    "pct_pisciforma",
    "pct_retreat_caddisfly",
    "pct_scrape",
    "pct_urban_intol",
    "rich_ephemeroptera",
    "rich_plecoptera",
    "rich_trichoptera")

# Southern Great Valley (SGV)
SGV_score <- SGV %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "gold",
    "pct_cling",
    "pct_collect",
    "pct_ephemeroptera_no_baetid",
    "pct_ept_no_hydro",
    "pct_ept_rich_no_tol",
    "pct_filter",
    "pct_heptageniidae",
    "pct_mod_tol_4_6",
    "pct_non_hydrop_trichoptera",
    "pct_pisciforma",
    "pct_predator",
    "pct_pterygota",
    "pct_scrape",
    "pct_sprawl",
    "pct_tolerant_7_10",
    "rich_collect",
    "rich_ephemeroptera",
    "rich_filter",
    "rich_trichoptera")

# Lower Northern Piedmont (LNP)
LNP_score <- LNP %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "aspt_mod",
    "pct_cling",
    "pct_collect",
    "pct_ept_rich",
    "pct_mod_tol_4_6",
    "pct_predator",
    "pct_pterygota",
    "rich_cling",
    "rich_ephemeroptera")

# Piedmont (PIED)
PIED_score <- PIED %>%
  select(
    "unique_id",
    "event_id",
    "sample_num",
    "icprb_bioregion_id",
    "station_id",
    "sample_date",
    "sample_time",
    "pct_cling",
    "pct_ept_rich",
    "pct_intol_0_4",
    "pct_tolerant_7_10",
    "pct_urban_intol",
    "rich_cling",
    "rich_ephemeroptera",
    "rich_trichoptera")
      
# Score the metrics
# NAPU Metric Scoring
NAPU_score$score_margalefs <- 
  case_when(
    NAPU_score$margalefs > 2.83 ~ 100,
    NAPU_score$margalefs < 2.74 ~ 0,
    TRUE ~ ((NAPU_score$margalefs - 2.74)/(2.83-2.74))*100)

NAPU_score$score_pct_cling <- 
  case_when(
    NAPU_score$pct_cling > 59.19 ~ 100,
    NAPU_score$pct_cling < 50.98 ~ 0,
    TRUE ~ ((NAPU_score$pct_cling-50.98)/(59.19-50.98))*100)

NAPU_score$score_pct_collect <- 
   case_when(
     NAPU_score$pct_collect < 71.84 ~ 100,
     NAPU_score$pct_collect > 82.8 ~ 0,
     TRUE ~ ((82.8-NAPU_score$pct_collect)/(82.8-71.84))*100)

NAPU_score$score_pct_ephemeroptera <- 
  case_when(
    NAPU_score$pct_ephemeroptera > 31.47 ~ 100,
    NAPU_score$pct_ephemeroptera < 19.62 ~ 0,
    TRUE ~ ((NAPU_score$pct_ephemeroptera-19.62)/(31.47-19.62))*100)

NAPU_score$score_pct_ept <- 
  case_when(
    NAPU_score$pct_ept > 62.26 ~ 100,
    NAPU_score$pct_ept < 54.08 ~ 0,
    TRUE ~ ((NAPU_score$pct_ept-54.08)/(62.26-54.08))*100)

NAPU_score$score_pct_ept_no_hydro <- 
  case_when(
    NAPU_score$pct_ept_no_hydro > 87.96 ~ 100,
    NAPU_score$pct_ept_no_hydro < 70.51 ~ 0,
    TRUE ~ ((NAPU_score$pct_ept_no_hydro-70.51)/(87.96-70.51))*100)

NAPU_score$score_pct_ept_rich_no_tol <- 
  case_when(
    NAPU_score$pct_ept_rich_no_tol > 45.32 ~ 100,
    NAPU_score$pct_ept_rich_no_tol < 32.85 ~ 0,
    TRUE ~ ((NAPU_score$pct_ept_rich_no_tol-32.85)/(45.32-32.85))*100)

NAPU_score$score_pct_filter <- 
  case_when(
    NAPU_score$pct_filter < 15.51 ~ 100,
    NAPU_score$pct_filter > 22.62 ~ 0,
    TRUE ~ ((22.62-NAPU_score$pct_filter)/(22.62-15.51))*100)

NAPU_score$score_pct_intol_0_3 <- 
  case_when(
    NAPU_score$pct_intol_0_3 > 44.7 ~ 100,
    NAPU_score$pct_intol_0_3 < 24.22 ~ 0,
    TRUE ~ ((NAPU_score$pct_intol_0_3-24.22)/(44.7-24.22))*100)

NAPU_score$score_pct_non_hydrop_trichoptera <-
  case_when(
    NAPU_score$pct_non_hydrop_trichoptera > 45.08 ~ 100,
    NAPU_score$pct_non_hydrop_trichoptera < 20.6 ~ 0,
    TRUE ~ ((NAPU_score$pct_non_hydrop_trichoptera-20.6)/(45.08-20.6))*100)

NAPU_score$score_pct_scrape <- 
  case_when(
    NAPU_score$pct_scrape > 9.36 ~ 100,
    NAPU_score$pct_scrape < 6.89 ~ 0,
    TRUE ~ ((NAPU_score$pct_scrape-6.89)/(9.36-6.89))*100)

NAPU_score$score_pielou <- 
  case_when(
    NAPU_score$pielou < 0.79 ~ 100,
    NAPU_score$pielou > 0.80 ~ 0,
    TRUE ~ ((0.80-NAPU_score$pielou)/(0.80-0.79))*100)

NAPU_score$score_rich_burrow <- 
  case_when(
    NAPU_score$rich_burrow > 2.95 ~ 100,
    NAPU_score$rich_burrow < 1.93 ~ 0,
    TRUE ~ ((NAPU_score$rich_burrow-1.93)/(2.95-1.93))*100)

NAPU_score$score_rich_cling <- 
  case_when(
    NAPU_score$rich_cling > 8.0 ~ 100,
    NAPU_score$rich_cling < 6.77 ~ 0,
    TRUE ~ ((NAPU_score$rich_cling-6.77)/(8.0-6.77))*100)

NAPU_score$score_rich_gather <- 
  case_when(
    NAPU_score$rich_gather < 5.0 ~ 100,
    NAPU_score$rich_gather > 6.01 ~ 0,
    TRUE ~ ((6.01-NAPU_score$rich_gather)/(6.01-5.0))*100)

NAPU_score$score_rich_modtol <- 
  case_when(
     NAPU_score$rich_modtol < 6.0 ~ 100,
     NAPU_score$rich_modtol > 7.03 ~ 0,
     TRUE ~ ((7.03-NAPU_score$rich_modtol)/(7.03-6.0))*100)

NAPU_score$score_rich_plecoptera <- 
  case_when(
    NAPU_score$rich_plecoptera > 2.13 ~ 100,
    NAPU_score$rich_plecoptera < 0.70 ~ 0,
    TRUE ~ ((NAPU_score$rich_plecoptera-0.70)/(2.13-0.70))*100)

NAPU_score$score_rich_shred <- 
  case_when(
    NAPU_score$rich_shred > 2.0 ~ 100,
    NAPU_score$rich_shred < 0.84 ~ 0,
    TRUE ~ ((NAPU_score$rich_shred-0.84)/(2.0-0.84))*100)

NAPU_score$score_rich_sprawl <- 
  case_when(
    NAPU_score$rich_sprawl < 1.0 ~ 100,
    NAPU_score$rich_sprawl > 2.3 ~ 0,
    TRUE ~ ((2.3-NAPU_score$rich_sprawl)/(2.3-1.0))*100)

# NCA Metric Scoring
NCA_score$score_aspt_mod <-
  case_when(
    NCA_score$aspt_mod > 7.54 ~ 100,
    NCA_score$aspt_mod < 6.67 ~ 0,
    TRUE ~ ((NCA_score$aspt_mod - 6.67)/(7.54-6.67))*100)
  
NCA_score$score_pct_cote <-
  case_when(
    NCA_score$pct_cote > 63.95 ~ 100,
    NCA_score$pct_cote < 47.71 ~ 0,
    TRUE ~ ((NCA_score$pct_cote - 47.71)/(63.95-47.71))*100)

NCA_score$score_pct_ephemeroptera <-
  case_when(
    NCA_score$pct_ephemeroptera > 40.73 ~ 100,
    NCA_score$pct_ephemeroptera < 9.02 ~ 0,
    TRUE ~ ((NCA_score$pct_ephemeroptera - 9.02)/(40.73-9.02))*100)

NCA_score$score_pct_heptageniidae <-
  case_when(
   NCA_score$pct_heptageniidae > 13.72 ~ 100,
   NCA_score$pct_heptageniidae  < 0 ~ 0,
   TRUE ~ ((NCA_score$pct_heptageniidae - 0)/(13.72-0))*100)

NCA_score$score_pct_limestone <-
  case_when(
    NCA_score$pct_limestone > 8.93 ~ 100,
    NCA_score$pct_limestone < 0 ~ 0,
    TRUE ~ ((NCA_score$pct_limestone - 0)/(8.93-0))*100)

NCA_score$score_rich_cling <-
  case_when(
    NCA_score$rich_cling > 10.0 ~ 100,
    NCA_score$rich_cling < 7.75 ~ 0,
    TRUE ~ ((NCA_score$rich_cling-7.75)/(10.0-7.75))*100)

NCA_score$score_rich_ephemeroptera <- 
  case_when(
    NCA_score$rich_ephemeroptera > 4.0 ~ 100,
    NCA_score$rich_ephemeroptera < 3.83 ~ 0,
    TRUE ~ ((NCA_score$rich_ephemeroptera - 3.83)/(4.0-3.83))*100)

NCA_score$score_rich_ept <-
  case_when(
    NCA_score$rich_ept > 12.0 ~ 100,
    NCA_score$rich_ept < 8.02 ~ 0,
    TRUE ~ ((NCA_score$rich_ept-8.02)/(12.0-8.02))*100)

NCA_score$score_rich_plecoptera <-
  case_when(
    NCA_score$rich_plecoptera > 4.04 ~ 100,
    NCA_score$rich_plecoptera < 3.45 ~ 0,
    TRUE ~ ((NCA_score$rich_plecoptera - 3.45)/(4.04-3.45))*100)

# CA Metric Scoring
CA_score$score_pct_ept_rich <-
  case_when(
    CA_score$pct_ept_rich > 66.82 ~ 100,
    CA_score$pct_ept_rich < 56.82 ~ 0,
    TRUE ~ ((CA_score$pct_ept_rich-56.82)/(66.82-56.82))*100)

CA_score$score_pct_euholognatha <-
  case_when(
    CA_score$pct_euholognatha > 17.98 ~ 100,
    CA_score$pct_euholognatha < 0.23 ~ 0,
    TRUE ~ ((CA_score$pct_euholognatha-0.23)/(17.98-0.23))*100)

CA_score$score_pct_heptageniidae <-
  case_when(
    CA_score$pct_heptageniidae > 6.69 ~ 100,
    CA_score$pct_heptageniidae < 0 ~ 0,
    TRUE ~ ((CA_score$pct_heptageniidae-0)/(6.69-0))*100)

CA_score$score_pct_hydro_ept <-
  case_when(
    CA_score$pct_hydro_ept < 12.5 ~ 100,
    CA_score$pct_hydro_ept > 21.73 ~ 0,
    TRUE ~ ((21.73-CA_score$pct_hydro_ept)/(21.73-12.5))*100)

CA_score$score_pct_mod_tol_4_6 <- 
  case_when(
    CA_score$pct_mod_tol_4_6 < 43.04 ~ 100,
    CA_score$pct_mod_tol_4_6 > 57.26 ~ 0,
    TRUE ~ ((57.26-CA_score$pct_mod_tol_4_6)/(57.26-43.04))*100)

CA_score$score_pct_non_hydrop_trichoptera <-
  case_when(
    CA_score$pct_non_hydrop_trichoptera > 40.4 ~ 100,
    CA_score$pct_non_hydrop_trichoptera < 25.02 ~ 0,
    TRUE ~ ((CA_score$pct_non_hydrop_trichoptera - 25.02)/(40.4-25.02))*100)

CA_score$score_pct_pisciforma <-
  case_when(
    CA_score$pct_pisciforma > 12.33 ~ 100,
    CA_score$pct_pisciforma < 5.49 ~ 0,
    TRUE ~ ((CA_score$pct_pisciforma-5.49)/(12.33-5.49))*100)

CA_score$score_pct_systellognatha <-
  case_when(
    CA_score$pct_systellognatha > 5.44 ~ 100,
    CA_score$pct_systellognatha < 0.08 ~ 0,
    TRUE ~ ((CA_score$pct_systellognatha-0.08)/(5.44-0.08))*100)

CA_score$score_rich_burrow <- 
  case_when(
    CA_score$rich_burrow > 3.0 ~ 100,
    CA_score$rich_burrow < 1.4 ~ 0,
    TRUE ~ ((CA_score$rich_burrow-1.4)/(3.0-1.4))*100)

CA_score$score_rich_collect <- 
  case_when(
    CA_score$rich_collect > 7.0 ~ 100,
    CA_score$rich_collect < 5.13 ~ 0,
    TRUE ~ ((CA_score$rich_collect-5.13)/(7.0-5.13))*100)

CA_score$score_rich_filter <-
  case_when(
    CA_score$rich_filter > 2.91 ~ 100,
    CA_score$rich_filter < 1.38 ~ 0,
    TRUE ~ ((CA_score$rich_filter-1.38)/(2.91-1.38))*100)

CA_score$score_rich_plecoptera <-
  case_when(
    CA_score$rich_plecoptera > 4.0 ~ 100,
    CA_score$rich_plecoptera < 0.47 ~ 0,
    TRUE ~ ((CA_score$rich_plecoptera-0.47)/(4.0-0.47))*100)

CA_score$score_rich_predator <- 
  case_when(
    CA_score$rich_predator > 3.0 ~ 100,
    CA_score$rich_predator < 1.44 ~ 0,
    TRUE ~ ((CA_score$rich_predator-1.44)/(3.0-1.44))*100)

# MAC Metric Scoring
MAC_score$score_aspt_mod <-
  case_when(
    MAC_score$aspt_mod > 3.27 ~ 100,
    MAC_score$aspt_mod < 2.9 ~ 0,
    TRUE ~ ((MAC_score$aspt_mod-2.9)/(3.27-2.9))*100)

MAC_score$score_gold <-
  case_when(
    MAC_score$gold > 58.96 ~ 100,
    MAC_score$gold < 33.91 ~ 0,
    TRUE ~ ((MAC_score$gold-33.91)/(58.96-33.91))*100)

MAC_score$score_pct_arthropoda <-
  case_when(
    MAC_score$pct_arthropoda < 74.01 ~ 100,
    MAC_score$pct_arthropoda > 95.38 ~ 0,
    TRUE ~ ((95.38-MAC_score$pct_arthropoda)/(95.38-74.01))*100)

MAC_score$score_pct_chironomidae <-
  case_when(
    MAC_score$pct_chironomidae < 23.01 ~ 100,
    MAC_score$pct_chironomidae > 42.68 ~ 0,
    TRUE ~ ((42.68-MAC_score$pct_chironomidae)/(42.68-23.01))*100)
  
MAC_score$score_pct_collect <-
  case_when(
    MAC_score$pct_collect < 73.25 ~ 100,
    MAC_score$pct_collect > 96.19 ~ 0,
    TRUE ~ ((96.19 - MAC_score$pct_collect)/(96.19-73.25))*100)

MAC_score$score_pct_mod_tol_4_6 <-
  case_when(
    MAC_score$pct_mod_tol_4_6 < 52.49 ~ 100,
    MAC_score$pct_mod_tol_4_6 > 75.48 ~ 0,
    TRUE ~ ((75.48-MAC_score$pct_mod_tol_4_6)/(75.48-52.49))*100)

MAC_score$score_pct_odonata <-
  case_when(
    MAC_score$pct_odonata > 1.82 ~ 100,
    MAC_score$pct_odonata < 0.43 ~ 0,
    TRUE ~ ((MAC_score$pct_odonata - 0.43)/(1.82-0.43))*100)

MAC_score$score_pct_predator <-
  case_when(
    MAC_score$pct_predator > 5.16 ~ 100,
    MAC_score$pct_predator < 4.01 ~ 0,
    TRUE ~ ((MAC_score$pct_predator - 4.01)/(5.16-4.01))*100)

MAC_score$score_pct_scrape <-
  case_when(
    MAC_score$pct_scrape > 12.07 ~ 100,
    MAC_score$pct_scrape < 0 ~ 0,
    TRUE ~ ((MAC_score$pct_scrape-0)/(12.07-0))*100)

MAC_score$score_pct_urban_intol <-
  case_when(
    MAC_score$pct_urban_intol < 65.28 ~ 100,
    MAC_score$pct_urban_intol > 71.78 ~ 0,
    TRUE ~ ((71.78-MAC_score$pct_urban_intol)/(71.78-65.28))*100)

MAC_score$score_rich_climb <-
  case_when(
    MAC_score$rich_climb > 2.45 ~ 100,
    MAC_score$rich_climb < 0 ~ 0,
    TRUE ~ ((MAC_score$rich_climb-0)/(2.45-0))*100)

MAC_score$score_rich_tol <-
  case_when(
    MAC_score$rich_tol > 4.0 ~ 100,
    MAC_score$rich_tol < 2.16 ~ 0,
    TRUE ~ ((MAC_score$rich_tol-2.16)/(4.0-2.16))*100)

# SEP Metric Scoring
SEP_score$score_aspt_mod <-
  case_when(
    SEP_score$aspt_mod > 4.65 ~ 100,
    SEP_score$aspt_mod < 3.18 ~ 0,
    TRUE ~ ((SEP_score$aspt_mod-3.18)/(4.65-3.18))*100)

SEP_score$score_gold <-
  case_when(
    SEP_score$gold > 50.3 ~ 100,
    SEP_score$gold < 32.16 ~ 0,
    TRUE ~ ((SEP_score$gold-32.16)/(50.3-32.16))*100)

SEP_score$score_hbi <-
  case_when(
    SEP_score$hbi < 5.12 ~ 100,
    SEP_score$hbi > 5.86 ~ 0,
    TRUE ~ ((5.86-SEP_score$hbi)/(5.86-5.12))*100)

SEP_score$pct_cling <-
  case_when(
    SEP_score$pct_cling > 43.05 ~ 100,
    SEP_score$pct_cling < 0 ~ 0,
    TRUE ~ ((SEP_score$pct_cling-0)/(43.05-0))*100)

SEP_score$score_pct_cote <-
  case_when(
    SEP_score$pct_cote > 26.37 ~ 100,
    SEP_score$pct_cote < 1.62 ~ 0,
    TRUE ~ ((SEP_score$pct_cote-1.62)/(26.37-1.62))*100)

SEP_score$score_pct_ept_rich_no_tol <-
  case_when(
    SEP_score$pct_ept_rich_no_tol > 24.73 ~ 100,
    SEP_score$pct_ept_rich_no_tol < 16.49 ~ 0,
    TRUE ~ ((SEP_score$pct_ept_rich_no_tol-16.49)/(24.73-16.49))*100)

SEP_score$score_rich_cling <-
  case_when(
    SEP_score$rich_cling > 4.93 ~ 100,
    SEP_score$rich_cling < 1.03 ~ 0,
    TRUE ~ ((SEP_score$rich_cling-1.03)/(4.93-1.03))*100)

SEP_score$score_rich_collect <-
  case_when(
    SEP_score$rich_collect > 8.0 ~ 100,
    SEP_score$rich_collect < 4.62 ~ 0,
    TRUE ~ ((SEP_score$rich_collect-4.62)/(8.0-4.62))*100)

SEP_score$score_rich_ephemeroptera <-
  case_when(
    SEP_score$rich_ephemeroptera > 2.0 ~ 100,
    SEP_score$rich_ephemeroptera < 0 ~ 0,
    TRUE ~ ((SEP_score$rich_ephemeroptera-0)/(2.0-0))*100)

SEP_score$score_rich_filter <-
  case_when(
    SEP_score$rich_filter  > 2.31 ~ 100,
    SEP_score$rich_filter < 0.04 ~ 0,
    TRUE ~ ((SEP_score$rich_filter-0.04)/(2.31-0.04))*100)

SEP_score$score_rich_trichoptera <-
  case_when(
    SEP_score$rich_trichoptera > 2.0 ~ 100,
    SEP_score$rich_trichoptera < 0.41 ~ 0,
    TRUE ~ ((SEP_score$rich_trichoptera-0.41)/(2.0-0.41))*100)

# BLUE Metric Scoring
BLUE_score$score_pct_burrow <-
  case_when(
    BLUE_score$pct_burrow < 12.65 ~ 100,
    BLUE_score$pct_burrow > 40.71 ~ 0,
    TRUE ~ ((40.71-BLUE_score$pct_burrow)/(40.71-12.65))*100)

BLUE_score$score_pct_ept_rich_no_tol <-
  case_when(
    BLUE_score$pct_ept_rich_no_tol > 52.78 ~ 100,
    BLUE_score$pct_ept_rich_no_tol < 34.74 ~ 0,
    TRUE ~ ((BLUE_score$pct_ept_rich_no_tol-34.74)/(52.78-34.74))*100)

BLUE_score$score_pct_scrape <-
  case_when(
    BLUE_score$pct_scrape > 15.23 ~ 100,
    BLUE_score$pct_scrape < 0 ~ 0,
    TRUE ~ ((BLUE_score$pct_scrape-0)/(15.23-0))*100)

BLUE_score$score_pct_systellognatha <-
  case_when(
    BLUE_score$pct_systellognatha > 6.06 ~ 100,
    BLUE_score$pct_systellognatha < 0 ~ 0,
    TRUE ~ ((BLUE_score$pct_systellognatha-0)/(6.06-0))*100)

BLUE_score$score_rich_ephemeroptera <-
  case_when(
    BLUE_score$rich_ephemeroptera > 4.0 ~ 100,
    BLUE_score$rich_ephemeroptera < 0.33 ~ 0,
    TRUE ~ ((BLUE_score$rich_ephemeroptera-0.33)/(4.0-0.33))*100)

# NRV Metric Scoring
NRV_score$score_aspt_mod <-
  case_when(
    NRV_score$aspt_mod > 6.27 ~ 100,
    NRV_score$aspt_mod < 4.59 ~ 0,
    TRUE ~ ((NRV_score$aspt_mod-4.59)/(6.27-4.59))*100)

NRV_score$score_pct_ephemeroptera_no_baetid <-
  case_when(
    NRV_score$pct_ephemeroptera_no_baetid > 23.69 ~ 100,
    NRV_score$pct_ephemeroptera_no_baetid < 6.01 ~ 0,
    TRUE ~ ((NRV_score$pct_ephemeroptera_no_baetid-6.01)/(23.69-6.01))*100)

NRV_score$score_pct_ept_rich <-
  case_when(
    NRV_score$pct_ept_rich > 64.7 ~ 100,
    NRV_score$pct_ept_rich < 47.53 ~ 0,
    TRUE ~ ((NRV_score$pct_ept_rich-47.53)/(64.7-47.53))*100)

NRV_score$score_rich_collect <-
  case_when(
    NRV_score$rich_collect > 8.0 ~ 100,
    NRV_score$rich_collect < 7.14 ~ 0,
    TRUE ~ ((NRV_score$rich_collect-7.14)/(8.0-7.14))*100)

NRV_score$score_rich_ephemeroptera <-
  case_when(
    NRV_score$rich_ephemeroptera > 4.0 ~ 100,
    NRV_score$rich_ephemeroptera < 1.8 ~ 0,
    TRUE ~ ((NRV_score$rich_ephemeroptera-1.8)/(4.0-1.8))*100)

NRV_score$score_rich_predator <-
  case_when(
    NRV_score$rich_predator > 3.0 ~ 100,
    NRV_score$rich_predator < 0.32 ~ 0,
    TRUE ~ ((NRV_score$rich_predator-0.32)/(3.0-0.32))*100)

NRV_score$score_rich_shred <-
  case_when(
    NRV_score$rich_shred > 2.0 ~ 100,
    NRV_score$rich_shred < 1.27 ~ 0,
    TRUE ~ ((NRV_score$rich_shred-1.27)/(2.0-1.27))*100)

NRV_score$score_rich_trichoptera <-
  case_when(
    NRV_score$rich_trichoptera > 3.0 ~ 100,
    NRV_score$rich_trichoptera < 2.53 ~ 0,
    TRUE ~ ((NRV_score$rich_trichoptera-2.53)/(3.0-2.53))*100)

# UNP Metric Scoring
UNP_score$score_hbi <-
  case_when(
    UNP_score$hbi < 4.01 ~ 100,
    UNP_score$hbi > 5.74 ~ 0,
    TRUE ~ ((5.74-UNP_score$hbi)/(5.74-4.01))*100)

UNP_score$score_pct_collect <-
  case_when(
    UNP_score$pct_collect < 80.32 ~ 100,
    UNP_score$pct_collect > 90.97 ~ 0,
    TRUE ~ ((90.97-UNP_score$pct_collect)/(90.97-80.32))*100)

UNP_score$score_pct_ept_rich_no_tol <-
  case_when(
    UNP_score$pct_ept_rich_no_tol > 37.09 ~ 100,
    UNP_score$pct_ept_rich_no_tol < 22.1 ~ 0,
    TRUE ~ ((UNP_score$pct_ept_rich_no_tol-22.1)/(37.09-22.1))*100)

UNP_score$score_pct_filter <-
  case_when(
    UNP_score$pct_filter > 18.14 ~ 100,
    UNP_score$pct_filter < 1.91 ~ 0,
    TRUE ~ ((UNP_score$pct_filter - 1.91)/(18.14-1.91))*100)

UNP_score$score_pct_hexapoda <-
  case_when(
    UNP_score$pct_hexapoda > 99.5 ~ 100,
    UNP_score$pct_hexapoda < 96.59 ~ 0,
    TRUE ~ ((UNP_score$pct_hexapoda-96.59)/(99.5-96.59))*100)

UNP_score$score_pct_pisciforma <-
  case_when(
    UNP_score$pct_pisciforma > 9.43 ~ 100,
    UNP_score$pct_pisciforma < 0 ~ 0,
    TRUE ~ ((UNP_score$pct_pisciforma-0)/(9.43-0))*100)

UNP_score$score_pct_retreat_caddisfly <-
  case_when(
    UNP_score$pct_retreat_caddisfly > 10.97 ~ 100,
    UNP_score$pct_retreat_caddisfly < 2.89 ~ 0,
    TRUE ~ ((UNP_score$pct_retreat_caddisfly-2.89)/(10.97-2.89))*100)

UNP_score$score_pct_scrape <-
  case_when(
    UNP_score$pct_scrape > 5.72 ~ 100,
    UNP_score$pct_scrape < 0.22 ~ 0,
    TRUE ~ ((UNP_score$pct_scrape-0.22)/(5.72-0.22))*100)

UNP_score$score_pct_urban_intol <- 
  case_when(
    UNP_score$pct_urban_intol > 98.46 ~ 100,
    UNP_score$pct_urban_intol < 91.71 ~ 0,
    TRUE ~ ((UNP_score$pct_urban_intol-91.71)/(98.46-91.71))*100)

UNP_score$score_rich_ephemeroptera <-
  case_when(
    UNP_score$rich_ephemeroptera > 3.0 ~ 100,
    UNP_score$rich_ephemeroptera < 1.44 ~ 0,
    TRUE ~ ((UNP_score$rich_ephemeroptera-1.44)/(3.0-1.44))*100)

UNP_score$score_rich_plecoptera <-
  case_when(
    UNP_score$rich_plecoptera > 2.23 ~ 100,
    UNP_score$rich_plecoptera < 0 ~ 0,
    TRUE ~ ((UNP_score$rich_plecoptera-0)/(2.23-0))*100)

UNP_score$score_rich_trichoptera <-
  case_when(
    UNP_score$rich_trichoptera > 3.0 ~ 100,
    UNP_score$rich_trichoptera < 1.01 ~ 0,
    TRUE ~ ((UNP_score$rich_trichoptera-1.01)/(3.0-1.01))*100)

# SRV Metric Scoring
SRV_score$score_aspt_mod <-
  case_when(
    SRV_score$aspt_mod > 6.44 ~ 100,
    SRV_score$aspt_mod < 4.95 ~ 0,
    TRUE ~ ((SRV_score$aspt_mod-4.95)/(6.44-4.95))*100)

SRV_score$score_pct_burrow <-
  case_when(
    SRV_score$pct_burrow < 17.13 ~ 100,
    SRV_score$pct_burrow > 31.28 ~ 0,
    TRUE ~ ((31.28-SRV_score$pct_burrow)/(31.28-17.13))*100)

SRV_score$score_pct_cling <-
  case_when(
    SRV_score$pct_cling > 58.45 ~ 100,
    SRV_score$pct_cling < 40.16 ~ 100,
    TRUE ~ ((SRV_score$pct_cling-40.16)/(58.45-40.16))*100)

SRV_score$score_pct_cote <-
  case_when(
    SRV_score$pct_cote > 57.55 ~ 100,
    SRV_score$pct_cote < 43.78 ~ 0,
    TRUE ~ ((SRV_score$pct_cote-43.78)/(57.55-43.78))*100)

SRV_score$score_pct_ephemeroptera_no_baetid <-
  case_when(
    SRV_score$pct_ephemeroptera_no_baetid > 21.0 ~ 100,
    SRV_score$pct_ephemeroptera_no_baetid < 2.8 ~ 0,
    TRUE ~ ((SRV_score$pct_ephemeroptera_no_baetid-2.8)/(21.0-2.8))*100)

SRV_score$score_pct_ept_rich_no_tol <-
  case_when(
    SRV_score$pct_ept_rich_no_tol > 47.16 ~ 100,
    SRV_score$pct_ept_rich_no_tol < 34.94 ~ 0,
    TRUE ~ ((SRV_score$pct_ept_rich_no_tol-34.94)/(47.16-34.94))*100)

SRV_score$score_pct_predator <-
  case_when(
    SRV_score$pct_predator > 7.12 ~ 100,
    SRV_score$pct_predator < 2.24 ~ 0,
    TRUE ~ ((SRV_score$pct_predator-2.24)/(7.12-2.24))*100)

SRV_score$score_pct_scrape <-
  case_when(
    SRV_score$pct_scrape > 10.88 ~ 100,
    SRV_score$pct_scrape < 0.47 ~ 0,
    TRUE ~ ((SRV_score$pct_scrape-0.47)/(10.88-0.47))*100)

SRV_score$score_rich_cling <- 
  case_when(
    SRV_score$rich_cling > 8.43 ~ 100,
    SRV_score$rich_cling < 6.16 ~ 0,
    TRUE ~ ((SRV_score$rich_cling-6.16)/(8.43-6.16))*100)

SRV_score$score_rich_collect <-
  case_when(
    SRV_score$rich_collect > 7.97 ~ 100,
    SRV_score$rich_collect < 6.02 ~ 0,
    TRUE ~ ((SRV_score$rich_collect-6.02)/(7.97-6.02))*100)

SRV_score$score_rich_ephemeroptera <-
  case_when(
    SRV_score$rich_ephemeroptera > 4.0 ~ 100,
    SRV_score$rich_ephemeroptera < 3.66 ~ 0,
    TRUE ~ ((SRV_score$rich_ephemeroptera-3.66)/(4.0-3.66))*100)

SRV_score$score_rich_intol <-
  case_when(
    SRV_score$rich_intol > 8.0 ~ 100,
    SRV_score$rich_intol < 4.15 ~ 0,
    TRUE ~ ((SRV_score$rich_intol-4.15)/(8.0-4.15))*100)

SRV_score$score_rich_plecoptera <-
  case_when(
    SRV_score$rich_plecoptera > 3.0 ~ 100,
    SRV_score$rich_plecoptera < 0.65 ~ 0,
    TRUE ~ ((SRV_score$rich_plecoptera-0.65)/(3.0-0.65))*100)

SRV_score$score_rich_predator <-
  case_when(
    SRV_score$rich_predator > 3.0 ~ 100,
    SRV_score$rich_predator < 2.72 ~ 0,
    TRUE ~ ((SRV_score$rich_predator-2.72)/(3.0-2.72))*100)

SRV_score$score_rich_trichoptera <-
  case_when(
    SRV_score$rich_trichoptera > 3.0 ~ 100,
    SRV_score$rich_trichoptera < 2.79 ~ 0,
    TRUE ~ ((SRV_score$rich_trichoptera-2.79)/(3.0-2.79))*100)

# SGV Metric Scoring
SGV_score$score_aspt_mod <-
  case_when(
    SGV_score$aspt_mod > 6.44 ~ 100,
    SGV_score$aspt_mod < 3.94 ~ 0,
    TRUE ~ ((SGV_score$aspt_mod-3.94)/(6.44-3.94))*100)

SGV_score$score_gold <-
  case_when(
    SGV_score$gold > 80.89 ~ 100,
    SGV_score$gold < 64.95 ~ 0,
    TRUE ~ ((SGV_score$gold-64.95)/(80.89-64.95))*100)

SGV_score$score_pct_cling <-
  case_when(
    SGV_score$pct_cling > 62.23 ~ 100,
    SGV_score$pct_cling < 39.7 ~ 0,
    TRUE ~ ((SGV_score$pct_cling-39.7)/(62.23-39.7))*100)

SGV_score$score_pct_collect <-
  case_when(
    SGV_score$pct_collect < 71.17 ~ 100,
    SGV_score$pct_collect > 94.57 ~ 0,
    TRUE ~ ((94.57-SGV_score$pct_collect)/(94.57-71.17))*100)

SGV_score$score_pct_ephemeroptera_no_baetid <-
  case_when(
    SGV_score$pct_ephemeroptera_no_baetid > 23.94 ~ 100,
    SGV_score$pct_ephemeroptera_no_baetid < 5.23 ~ 0,
    TRUE ~ ((SGV_score$pct_ephemeroptera_no_baetid-5.23)/(23.94-5.23))*100)

SGV_score$score_pct_ept_no_hydro <-
  case_when(
    SGV_score$pct_ept_no_hydro > 83.21 ~ 100,
    SGV_score$pct_ept_no_hydro < 73.53 ~ 0,
    TRUE ~ ((SGV_score$pct_ept_no_hydro-73.53)/(83.21-73.53))*100)

SGV_score$score_pct_ept_rich_no_tol <-
  case_when(
    SGV_score$pct_ept_rich_no_tol > 32.97 ~ 100,
    SGV_score$pct_ept_rich_no_tol < 19.39 ~ 0,
    TRUE ~ ((SGV_score$pct_ept_rich_no_tol-19.39)/(32.97-19.39))*100)

SGV_score$score_pct_filter <-
  case_when(
    SGV_score$pct_filter > 22.79 ~ 100,
    SGV_score$pct_filter < 8.6 ~ 0,
    TRUE ~ ((SGV_score$pct_filter-8.6)/(22.79-8.6))*100)

SGV_score$score_pct_heptageniidae <-
  case_when(
    SGV_score$pct_heptageniidae > 7.89 ~ 100,
    SGV_score$pct_heptageniidae < 0 ~ 0,
    TRUE ~ ((SGV_score$pct_heptageniidae-0)/(7.89-0))*100)

SGV_score$score_pct_mod_tol_4_6 <-
  case_when(
    SGV_score$pct_mod_tol_4_6 < 52.49 ~ 100,
    SGV_score$pct_mod_tol_4_6 > 76.71 ~ 0,
    TRUE ~ ((76.71-SGV_score$pct_mod_tol_4_6)/(76.71-52.49))*100)

SGV_score$score_pct_non_hydrop_trichoptera <-
  case_when(
    SGV_score$pct_non_hydrop_trichoptera > 30.54 ~ 100,
    SGV_score$pct_non_hydrop_trichoptera < 10.57 ~ 0,
    TRUE ~ ((SGV_score$pct_non_hydrop_trichoptera-10.57)/(30.54-10.57))*100)

SGV_score$score_pct_pisciforma <-
  case_when(
    SGV_score$pct_pisciforma > 17.07 ~ 100,
    SGV_score$pct_pisciforma < 0.1 ~ 0,
    TRUE ~ ((SGV_score$pct_pisciforma-0.1)/(17.07-0.1))*100)

SGV_score$score_pct_predator <-
  case_when(
    SGV_score$pct_predator > 5.28 ~ 100,
    SGV_score$pct_predator < 0.02 ~ 0,
    TRUE ~ ((SGV_score$pct_predator-0.02)/(5.28-0.02))*100)

SGV_score$score_pct_pterygota <-
  case_when(
    SGV_score$pct_pterygota > 96.88 ~ 100,
    SGV_score$pct_pterygota < 90.2 ~ 0,
    TRUE ~ ((SGV_score$pct_pterygota-90.2)/(96.88-90.2))*100)

SGV_score$score_pct_scrape <-
  case_when(
    SGV_score$pct_scrape > 15.43 ~ 100,
    SGV_score$pct_scrape < 0.32 ~ 0,
    TRUE ~ ((SGV_score$pct_scrape-0.32)/(15.43-0.32))*100)

SGV_score$score_pct_sprawl <-
  case_when(
    SGV_score$pct_sprawl < 1.79 ~ 100,
    SGV_score$pct_sprawl > 4.54 ~ 0,
    TRUE ~ ((4.54-SGV_score$pct_sprawl)/(4.54-1.79))*100)

SGV_score$score_pct_tolerant_7_10 <-
  case_when(
    SGV_score$pct_tolerant_7_10 < 1.73 ~ 100,
    SGV_score$pct_tolerant_7_10 > 4.3 ~ 0,
    TRUE ~ ((4.3-SGV_score$pct_tolerant_7_10)/(4.3-1.73))*100)

SGV_score$score_rich_collect <-
  case_when(
    SGV_score$rich_collect > 8.0 ~ 100,
    SGV_score$rich_collect < 6.32 ~ 0,
    TRUE ~ ((SGV_score$rich_collect-6.32)/(8.0-6.32))*100)

SGV_score$score_rich_ephemeroptera <-
  case_when(
    SGV_score$rich_ephemeroptera > 3.94 ~ 100,
    SGV_score$rich_ephemeroptera < 0.61 ~ 0,
    TRUE ~ ((SGV_score$rich_ephemeroptera-0.61)/(3.94-0.61))*100)

SGV_score$score_rich_filter <-
  case_when(
    SGV_score$rich_filter > 3.0 ~ 100,
    SGV_score$rich_filter < 1.36 ~ 0,
    TRUE ~ ((SGV_score$rich_filter-1.36)/(3.0-1.36))*100)

SGV_score$score_rich_trichoptera <-
  case_when(
    SGV_score$rich_trichoptera > 2.54 ~ 100,
    SGV_score$rich_trichoptera < 0.08 ~ 0,
    TRUE ~ ((SGV_score$rich_trichoptera-0.08)/(2.54-0.08))*100)

# LNP Metric Scoring
LNP_score$score_aspt_mod <-
  case_when(
    LNP_score$aspt_mod > 6.62 ~ 100,
    LNP_score$aspt_mod < 2.7 ~ 0,
    TRUE ~ ((LNP_score$aspt_mod-2.7)/(6.62-2.7))*100)

LNP_score$score_pct_cling <-
  case_when(
    LNP_score$pct_cling > 62.77 ~ 100,
    LNP_score$pct_cling < 4.54 ~ 0,
    TRUE ~ ((LNP_score$pct_cling-4.54)/(62.77-4.54))*100)

LNP_score$score_pct_collect <-
  case_when(
    LNP_score$pct_collect < 72.82 ~ 100,
    LNP_score$pct_collect > 92.49 ~ 0,
    TRUE ~ ((92.49-LNP_score$pct_collect)/(92.49-72.82))*100)

LNP_score$score_pct_ept_rich <-
  case_when(
    LNP_score$pct_ept_rich > 52.32 ~ 100,
    LNP_score$pct_ept_rich < 38.07 ~ 0,
    TRUE ~ ((LNP_score$pct_ept_rich-38.07)/(52.32-38.07))*100)

LNP_score$score_pct_mod_tol_4_6 <-
  case_when(
    LNP_score$pct_mod_tol_4_6 < 46.54 ~ 100,
    LNP_score$pct_mod_tol_4_6 > 77.78 ~ 0,
    TRUE ~ ((77.78-LNP_score$pct_mod_tol_4_6)/(77.78-46.54))*100)

LNP_score$score_pct_predator <-
  case_when(
    LNP_score$pct_predator > 7.78 ~ 100,
    LNP_score$pct_predator < 1.43 ~ 0,
    TRUE ~ ((LNP_score$pct_predator-1.43)/(7.78-1.43))*100)

LNP_score$score_pct_pterygota <-
  case_when(
    LNP_score$pct_pterygota > 98.36 ~ 100,
    LNP_score$pct_pterygota < 92.09 ~ 0,
    TRUE ~ ((LNP_score$pct_pterygota-92.09)/(98.36-92.09))*100)

LNP_score$score_rich_cling <-
  case_when(
    LNP_score$rich_cling > 7.0 ~ 100,
    LNP_score$rich_cling < 3.69 ~ 0,
    TRUE ~ ((LNP_score$rich_cling-3.69)/(7.0-3.69))*100)

LNP_score$score_rich_ephemeroptera <-
  case_when(
    LNP_score$rich_ephemeroptera > 3.0 ~ 100,
    LNP_score$rich_ephemeroptera < 1.7 ~ 0,
    TRUE ~ ((LNP_score$rich_ephemeroptera-1.7)/(3.0-1.7))*100)

# PIED Metric Scoring
PIED_score$score_pct_cling <-
  case_when(
    PIED_score$pct_cling > 62.62 ~ 100,
    PIED_score$pct_cling < 32.33 ~ 0,
    TRUE ~ ((PIED_score$pct_cling-32.33)/(62.62-32.33))*100)

PIED_score$score_pct_ept_rich <-
  case_when(
    PIED_score$pct_ept_rich > 53.58 ~ 100,
    PIED_score$pct_ept_rich < 38.51 ~ 0,
    TRUE ~ ((PIED_score$pct_ept_rich-38.51)/(53.58-38.51))*100)

PIED_score$score_pct_intol_0_4 <-
  case_when(
    PIED_score$pct_intol_0_4 > 58.15 ~ 100,
    PIED_score$pct_intol_0_4 < 27.97 ~ 0,
    TRUE ~ ((PIED_score$pct_intol_0_4-27.97)/(58.15-27.97))*100)

PIED_score$score_pct_tolerant_7_10 <- 
  case_when(
    PIED_score$pct_tolerant_7_10 < 1.6 ~ 100,
    PIED_score$pct_tolerant_7_10 > 4.84 ~ 0,
    TRUE ~ ((4.84-PIED_score$pct_tolerant_7_10)/(4.84-1.6))*100)

PIED_score$score_pct_urban_intol <-
  case_when(
    PIED_score$pct_urban_intol > 95.41 ~ 100,
    PIED_score$pct_urban_intol < 86.93 ~ 0,
    TRUE ~ ((PIED_score$pct_urban_intol-86.93)/(95.41-86.93))*100)

PIED_score$score_rich_cling <-
  case_when(
    PIED_score$rich_cling > 8.0 ~ 100,
    PIED_score$rich_cling < 2.96 ~ 0,
    TRUE ~ ((PIED_score$rich_cling-2.96)/(8.0-2.96))*100)
  
PIED_score$score_rich_ephemeroptera <-  
  case_when(
    PIED_score$rich_ephemeroptera > 3.6 ~ 100,
    PIED_score$rich_ephemeroptera < 0.86 ~ 0,
    TRUE ~ ((PIED_score$rich_ephemeroptera-0.86)/(3.6-0.86))*100)

PIED_score$score_rich_trichoptera <-
  case_when(
    PIED_score$rich_trichoptera > 2.03 ~ 100,
    PIED_score$rich_trichoptera < 0.45 ~ 0,
    TRUE ~ ((PIED_score$rich_trichoptera-0.45)/(2.03-0.45))*100)
      
# Average scores to get the Chessie BIBI
NAPU_score$chessie_bibi <- rowMeans(NAPU_score[ ,27:45], na.rm = T)
NCA_score$chessie_bibi  <- rowMeans(NCA_score[ ,17:25], na.rm = T)
CA_score$chessie_bibi   <- rowMeans(CA_score[ ,21:33], na.rm = T)
MAC_score$chessie_bibi  <- rowMeans(MAC_score[ ,20:31], na.rm = T)
SEP_score$chessie_bibi  <- rowMeans(SEP_score[ ,19:28], na.rm = T)
BLUE_score$chessie_bibi <- rowMeans(BLUE_score[ ,13:17], na.rm = T) 
NRV_score$chessie_bibi  <- rowMeans(NRV_score[ ,16:23], na.rm = T)
SRV_score$chessie_bibi  <- rowMeans(SRV_score[ ,23:37], na.rm = T)
UNP_score$chessie_bibi  <- rowMeans(UNP_score[ ,20:31], na.rm = T)
SGV_score$chessie_bibi  <- rowMeans(SGV_score[ ,29:49], na.rm = T) 
LNP_score$chessie_bibi  <- rowMeans(LNP_score[ ,17:25], na.rm = T)
PIED_score$chessie_bibi <- rowMeans(PIED_score[ ,16:23], na.rm = T) 
      
# Assign narrative ratings
NAPU_score$rating <-
  case_when(
    NAPU_score$chessie_bibi < 17.9 ~ "very_poor",
    NAPU_score$chessie_bibi >= 17.9 & NAPU_score$chessie_bibi < 35.9 ~ "poor",
    NAPU_score$chessie_bibi >= 35.9 & NAPU_score$chessie_bibi < 47.4 ~ "fair",
    NAPU_score$chessie_bibi >= 47.4 & NAPU_score$chessie_bibi < 61.9 ~ "good",
    NAPU_score$chessie_bibi >= 61.9 ~ "excellent",
    TRUE ~ "ERROR")

NCA_score$rating <-
  case_when(
    NCA_score$chessie_bibi < 15.7 ~ "very_poor",
    NCA_score$chessie_bibi >= 15.7 & NCA_score$chessie_bibi < 31.5 ~ "poor",
    NCA_score$chessie_bibi >= 31.5 & NCA_score$chessie_bibi < 56.3 ~ "fair",
    NCA_score$chessie_bibi >= 56.3 & NCA_score$chessie_bibi < 78.7 ~ "good",
    NCA_score$chessie_bibi >= 78.7 ~ "excellent",
    TRUE ~ "ERROR")
  
CA_score$rating <-
  case_when(
    CA_score$chessie_bibi < 27.9 ~ "very_poor",
    CA_score$chessie_bibi >= 27.9 & CA_score$chessie_bibi < 55.8 ~ "poor",
    CA_score$chessie_bibi >= 55.8 & CA_score$chessie_bibi < 69.5 ~ "fair",
    CA_score$chessie_bibi >= 69.5 & CA_score$chessie_bibi < 78.6 ~ "good",
    CA_score$chessie_bibi >= 78.6 ~ "excellent",
    TRUE ~ "ERROR")

MAC_score$rating <-
  case_when(
    MAC_score$chessie_bibi < 22.7 ~ "very_poor",
    MAC_score$chessie_bibi >= 22.7 & MAC_score$chessie_bibi < 45.4 ~ "poor",
    MAC_score$chessie_bibi >= 45.4 & MAC_score$chessie_bibi < 63.2 ~ "fair",
    MAC_score$chessie_bibi >= 63.2 & MAC_score$chessie_bibi < 76.8 ~ "good",
    MAC_score$chessie_bibi >= 76.8 ~ "excellent",
    TRUE ~ "ERROR")
  
SEP_score$rating <-
  case_when(
    SEP_score$chessie_bibi < 16.3 ~ "very_poor",
    SEP_score$chessie_bibi >= 16.3 & SEP_score$chessie_bibi < 32.6 ~ "poor",
    SEP_score$chessie_bibi >= 32.6 & SEP_score$chessie_bibi < 56.7 ~ "fair",
    SEP_score$chessie_bibi >= 56.7 & SEP_score$chessie_bibi < 83.9 ~ "good",
    SEP_score$chessie_bibi >= 83.9 ~ "excellent",
    TRUE ~ "ERROR")
  
BLUE_score$rating <-
  case_when(
    BLUE_score$chessie_bibi < 30.9 ~ "very_poor",
    BLUE_score$chessie_bibi >= 30.9 & BLUE_score$chessie_bibi < 61.7 ~ "poor",
    BLUE_score$chessie_bibi >= 61.7 & BLUE_score$chessie_bibi < 82.2 ~ "fair",
    BLUE_score$chessie_bibi >= 82.2 & BLUE_score$chessie_bibi < 92.1 ~ "good",
    BLUE_score$chessie_bibi >= 92.1 ~ "excellent",
    TRUE ~ "ERROR")
  
NRV_score$rating <-
  case_when(
    NRV_score$chessie_bibi < 19.1 ~ "very_poor",
    NRV_score$chessie_bibi >= 19.1 & NRV_score$chessie_bibi < 38.2 ~ "poor",
    NRV_score$chessie_bibi >= 38.2 & NRV_score$chessie_bibi < 50.8 ~ "fair",
    NRV_score$chessie_bibi >= 50.8 & NRV_score$chessie_bibi < 75.0 ~ "good",
    NRV_score$chessie_bibi >= 75.0 ~ "excellent",
    TRUE ~ "ERROR")
  
SRV_score$rating <-
  case_when(
    SRV_score$chessie_bibi < 21.6 ~ "very_poor",
    SRV_score$chessie_bibi >= 21.6 & SRV_score$chessie_bibi < 43.2 ~ "poor",
    SRV_score$chessie_bibi >= 43.2 & SRV_score$chessie_bibi < 58.0 ~ "fair",
    SRV_score$chessie_bibi >= 58.0 & SRV_score$chessie_bibi < 71.9 ~ "good",
    SRV_score$chessie_bibi >= 71.9 ~ "excellent",
    TRUE ~ "ERROR")

UNP_score$rating <-
  case_when(
    UNP_score$chessie_bibi < 31.3 ~ "very_poor",
    UNP_score$chessie_bibi >= 31.3 & UNP_score$chessie_bibi < 62.6 ~ "poor",
    UNP_score$chessie_bibi >= 62.6 & UNP_score$chessie_bibi < 69.9 ~ "fair",
    UNP_score$chessie_bibi >= 69.9 & UNP_score$chessie_bibi < 80.5 ~ "good",
    UNP_score$chessie_bibi >= 80.5 ~ "excellent",
    TRUE ~ "ERROR")

SGV_score$rating <-
  case_when(
    SGV_score$chessie_bibi < 29.9 ~ "very_poor",
    SGV_score$chessie_bibi >= 29.9 & SGV_score$chessie_bibi < 59.9 ~ "poor",
    SGV_score$chessie_bibi >= 59.9 & SGV_score$chessie_bibi < 66.0 ~ "fair",
    SGV_score$chessie_bibi >= 66.0 & SGV_score$chessie_bibi < 76.5 ~ "good",
    SGV_score$chessie_bibi >= 76.5 ~ "excellent",
    TRUE ~ "ERROR")

LNP_score$rating <-
  case_when(
    LNP_score$chessie_bibi < 35.2 ~ "very_poor",
    LNP_score$chessie_bibi >= 35.2 & LNP_score$chessie_bibi < 70.3 ~ "poor",
    LNP_score$chessie_bibi >= 70.3 & LNP_score$chessie_bibi < 80.2 ~ "fair",
    LNP_score$chessie_bibi >= 80.2 & LNP_score$chessie_bibi < 91.3 ~ "good",
    LNP_score$chessie_bibi >= 91.3 ~ "excellent",
    TRUE ~ "ERROR")

PIED_score$rating <-
  case_when(
    PIED_score$chessie_bibi < 30.3 ~ "very_poor",
    PIED_score$chessie_bibi >= 30.3 & PIED_score$chessie_bibi < 60.6 ~ "poor",
    PIED_score$chessie_bibi >= 60.6 & PIED_score$chessie_bibi < 73.2 ~ "fair",
    PIED_score$chessie_bibi >= 73.2 & PIED_score$chessie_bibi < 81.8 ~ "good",
    PIED_score$chessie_bibi >= 81.8 ~ "excellent",
    TRUE ~ "ERROR")

bind1 <- bind_rows(NAPU_score, NCA_score)
bind2 <- bind_rows(bind1, CA_score)
bind3 <- bind_rows(bind2, MAC_score)
bind4 <- bind_rows(bind3, SEP_score)
bind5 <- bind_rows(bind4, BLUE_score)
bind6 <- bind_rows(bind5, NRV_score)
bind7 <- bind_rows(bind6, SRV_score)
bind8 <- bind_rows(bind7, UNP_score)
bind9 <- bind_rows(bind8, SGV_score)
bind10 <- bind_rows(bind9, LNP_score)
bibi_ratings_combined <- bind_rows(bind10, PIED_score)

bibi_ratings_combined <- bibi_ratings_combined %>%
  separate(unique_id, c('event_id', 'sample_num'), sep="_", remove = FALSE)

final_score <- bibi_ratings_combined 

return(final_score)
 }
```
### **3. Program repetition**
Now that the Chessie BIBI program has been incorporated into a function, it will be repeated fifty times. This will likely take several hours, so you may want to let the program run overnight to avoid slowing down your computer while doing other tasks.      

If you would prefer to repeat the program either greater than or fewer than fifty times, simple change `50` to your own number in `repeat_me <- 50`.
```{r message=FALSE, warning=FALSE}
non_rare <- taxa.df 

repeat.scores.df <- non_rare %>%              
 select(unique_id) %>%
 unique() %>%
 arrange(unique_id)

sc.df <- repeat.scores.df
met.df <- repeat.scores.df

repeat_me <- 3

for(i in 1:repeat_me) {

  final_score <- ChessieBIBI_score()
  final_score <- final_score %>% select(unique_id, chessie_bibi)
  sc.df <-  full_join(sc.df, final_score, by = "unique_id")
  colnames(sc.df)[colnames(sc.df)=="chessie_bibi"] <- as.character(paste0("chessie_bibi", i))
  
  final_metric <- ChessieBIBI_score()
  final_metric <- bibi_ratings_combined %>% select(starts_with("unique_id"), starts_with("margalefs"), starts_with("pct"), starts_with("pielou"),
                  starts_with("rich"), starts_with("aspt_mod"), starts_with("gold"), starts_with("hbi"))
  final_metric <- final_metric %>% rename_at(vars(-unique_id), ~ paste0(., "_metric"))
  met_test.df <-  full_join(met.df, final_metric, by = "unique_id")
  met_test.df <- met_test.df %>% rename_at(vars(-unique_id), ~ paste0(., i))   # THIS LINE IS THE CULPRIT
  }

```
### **4. Prep the dataframes and assign narrative ratings**  
First, add the bioregion assignments to *ratings.df*, the data frame produced in Step 3 that contains the repeated scores.    

Then, the Chessie BIBI scores in *ratings.df* will be assign the Chessie BIBI scores a rating using a `mutate_at` statement.    

Last, join the scores and ratings together in one data frame, *join.df*.
```{r}
bioregions <- non_rare %>%
  select(icprb_bioregion_id, unique_id) %>%
  unique()

ratings.df <- sc.df

ratings.df2 <- full_join(ratings.df, bioregions, by = "unique_id")
ratings.df2 <- ratings.df2 %>%  
  select(icprb_bioregion_id, everything())

ratings.df2 <- ratings.df2 %>%
  mutate_at(vars(starts_with("chessie_")), list( 
  ~case_when(
    ratings.df2$icprb_bioregion_id == "napu" & . < 17.9 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "napu" & (. >= 17.9 & .< 35.9) ~ "poor",
    ratings.df2$icprb_bioregion_id == "napu" & (. >= 35.9 & .< 47.4) ~ "fair",
    ratings.df2$icprb_bioregion_id == "napu" & (. >= 47.4 & .< 61.9) ~ "good",
    ratings.df2$icprb_bioregion_id == "napu" & . >= 61.9 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "nca" & . < 15.7 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "nca" & (. >= 15.7 & .< 31.5) ~ "poor",
    ratings.df2$icprb_bioregion_id == "nca" & (. >= 31.5 & .< 56.3) ~ "fair",
    ratings.df2$icprb_bioregion_id == "nca" & (. >= 56.3 & .< 78.7) ~ "good",
    ratings.df2$icprb_bioregion_id == "nca" & . >= 78.7 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "ca" & . < 27.9 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "ca" & (. >= 27.9 & .< 55.8) ~ "poor",
    ratings.df2$icprb_bioregion_id == "ca" & (. >= 55.8 & .< 69.5) ~ "fair",
    ratings.df2$icprb_bioregion_id == "ca" & (. >= 69.5 & .< 78.6)~ "good",
    ratings.df2$icprb_bioregion_id == "ca" & . >= 78.6 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "mac" & . < 22.7 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "mac" & (. >= 22.7 & .< 45.4) ~ "poor",
    ratings.df2$icprb_bioregion_id == "mac" & (. >= 45.4 & .< 63.2) ~ "fair",
    ratings.df2$icprb_bioregion_id == "mac" & (. >= 63.2 & .< 76.8) ~ "good",
    ratings.df2$icprb_bioregion_id == "mac" & . >= 76.8 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "sep" & . < 16.3 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "sep" & (. >= 16.3 & .< 32.6) ~ "poor",
    ratings.df2$icprb_bioregion_id == "sep" & (. >= 32.6 & .< 56.7) ~ "fair",
    ratings.df2$icprb_bioregion_id == "sep" & (. >= 56.7 & .< 83.9) ~ "good",
    ratings.df2$icprb_bioregion_id == "sep" & . >= 83.9 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "blue" & . < 30.9 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "blue" & (. >= 30.9 & .< 61.7) ~ "poor",
    ratings.df2$icprb_bioregion_id == "blue" & (. >= 61.7 & .< 82.2) ~ "fair",
    ratings.df2$icprb_bioregion_id == "blue" & (. >= 82.2 & .< 92.1) ~ "good",
    ratings.df2$icprb_bioregion_id == "blue" & . >= 92.1 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "nrv" & . < 19.1 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "nrv" & (. >= 19.1 & .< 38.2) ~ "poor",
    ratings.df2$icprb_bioregion_id == "nrv" & (. >= 38.2 & .< 50.8)~ "fair",
    ratings.df2$icprb_bioregion_id == "nrv" & (. >= 50.8 & .< 75.0) ~ "good",
    ratings.df2$icprb_bioregion_id == "nrv" & . >= 75.0 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "srv" & . < 21.6 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "srv" & (. >= 21.6 & .< 43.2) ~ "poor",
    ratings.df2$icprb_bioregion_id == "srv" & (. >= 43.2 & .< 58.0) ~ "fair",
    ratings.df2$icprb_bioregion_id == "srv" & (. >= 58.0 & .< 71.9) ~ "good",
    ratings.df2$icprb_bioregion_id == "srv" & . >= 71.9 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "unp" & . < 31.3 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "unp" & (. >= 31.3 & .< 62.6) ~ "poor",
    ratings.df2$icprb_bioregion_id == "unp" & (. >= 62.6 & .< 69.9) ~ "fair",
    ratings.df2$icprb_bioregion_id == "unp" & (. >= 69.9 & .< 80.5) ~ "good",
    ratings.df2$icprb_bioregion_id == "unp" & . >= 80.5 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "sgv" & . < 29.9 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "sgv" & (. >= 29.9 & .< 59.9) ~ "poor",
    ratings.df2$icprb_bioregion_id == "sgv" & (. >= 59.9 & .< 66.0) ~ "fair",
    ratings.df2$icprb_bioregion_id == "sgv" & (. >= 66.0 & .< 76.5) ~ "good",
    ratings.df2$icprb_bioregion_id == "sgv" & . >= 76.5 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "lnp" & . < 35.2 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "lnp" & (. >= 35.2 & .< 70.3) ~ "poor",
    ratings.df2$icprb_bioregion_id == "lnp" & (. >= 70.3 & .< 80.2) ~ "fair",
    ratings.df2$icprb_bioregion_id == "lnp" & (. >= 80.2 & .< 91.3) ~ "good",
    ratings.df2$icprb_bioregion_id == "lnp" & . >= 91.3 ~ "excellent",
    
    ratings.df2$icprb_bioregion_id == "pied" & . < 30.3 ~ "very_poor",
    ratings.df2$icprb_bioregion_id == "pied" & (. >= 30.3 & .< 60.6) ~ "poor",
    ratings.df2$icprb_bioregion_id == "pied" & (. >= 60.6 & .< 73.2) ~ "fair",
    ratings.df2$icprb_bioregion_id == "pied" & (. >= 73.2 & .< 81.8) ~ "good",
    ratings.df2$icprb_bioregion_id == "pied" & . >= 81.8 ~ "excellent",
    TRUE ~ "ERROR")
    ))

names(ratings.df2)[3:102] <- paste0(c("rating"),1:100)

ChessieBIBI_repeated_ratings <- ratings.df2
ChessieBIBI_repeated_scores <- sc.df

join.df <- full_join(ChessieBIBI_repeated_scores, ChessieBIBI_repeated_ratings, by="unique_id")

join.df <- join.df %>%
  select(icprb_bioregion_id, everything())
```
###**5. Statistical analysis**
Determine the mean and median ratings of the fifty program repeatitions. This step will also calculate how often the mean or median rating occurs out of the twenty runs, as well as a comparison of whether or not the median and mean has the same rating. 
```{r warning=F, message=F}
stats.df <- join.df
stats.df$very_poor <- rowSums(stats.df[ ,103:202] == "very_poor")
stats.df$poor = rowSums(stats.df[,103:202] == "poor")
stats.df$fair = rowSums(stats.df[,103:202] == "fair")
stats.df$good = rowSums(stats.df[,103:202] == "good")
stats.df$excellent = rowSums(stats.df[,103:202] == "excellent")
stats.df$median_score = apply(stats.df[ ,3:102],1, median)
stats.df$median_rating <- 
   case_when(
    stats.df$icprb_bioregion_id == "napu" & stats.df$median_score < 17.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "napu" & (stats.df$median_score >= 17.9 & stats.df$median_score < 35.9) ~ "poor",
    stats.df$icprb_bioregion_id == "napu" & (stats.df$median_score >= 35.9 & stats.df$median_score < 47.4) ~ "fair",
    stats.df$icprb_bioregion_id == "napu" & (stats.df$median_score >= 47.4 & stats.df$median_score < 61.9) ~ "good",
    stats.df$icprb_bioregion_id == "napu" & stats.df$median_score >= 61.9 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "nca" & stats.df$median_score < 15.7 ~ "very_poor",
    stats.df$icprb_bioregion_id == "nca" & (stats.df$median_score >= 15.7 & stats.df$median_score < 31.5) ~ "poor",
    stats.df$icprb_bioregion_id == "nca" & (stats.df$median_score >= 31.5 & stats.df$median_score < 56.3) ~ "fair",
    stats.df$icprb_bioregion_id == "nca" & (stats.df$median_score >= 56.3 & stats.df$median_score < 78.7) ~ "good",
    stats.df$icprb_bioregion_id == "nca" & stats.df$median_score >= 78.7 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "ca" & stats.df$median_score < 27.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "ca" & (stats.df$median_score >= 27.9 & stats.df$median_score < 55.8) ~ "poor",
    stats.df$icprb_bioregion_id == "ca" & (stats.df$median_score>= 55.8 & stats.df$median_score < 69.5) ~ "fair",
    stats.df$icprb_bioregion_id == "ca" & (stats.df$median_score>= 69.5 & stats.df$median_score < 78.6)~ "good",
    stats.df$icprb_bioregion_id == "ca" & stats.df$median_score>= 78.6 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "mac" & stats.df$median_score < 22.7 ~ "very_poor",
    stats.df$icprb_bioregion_id == "mac" & (stats.df$median_score>= 22.7 & stats.df$median_score < 45.4) ~ "poor",
    stats.df$icprb_bioregion_id == "mac" & (stats.df$median_score>= 45.4 & stats.df$median_score < 63.2) ~ "fair",
    stats.df$icprb_bioregion_id == "mac" & (stats.df$median_score>= 63.2 & stats.df$median_score < 76.8) ~ "good",
    stats.df$icprb_bioregion_id == "mac" & stats.df$median_score>= 76.8 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "sep" & stats.df$median_score < 16.3 ~ "very_poor",
    stats.df$icprb_bioregion_id == "sep" & (stats.df$median_score>= 16.3 & stats.df$median_score < 32.6) ~ "poor",
    stats.df$icprb_bioregion_id == "sep" & (stats.df$median_score>= 32.6 & stats.df$median_score < 56.7) ~ "fair",
    stats.df$icprb_bioregion_id == "sep" & (stats.df$median_score>= 56.7 & stats.df$median_score < 83.9) ~ "good",
    stats.df$icprb_bioregion_id == "sep" & stats.df$median_score>= 83.9 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "blue" & stats.df$median_score < 30.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "blue" & (stats.df$median_score >= 30.9 & stats.df$median_score < 61.7) ~ "poor",
    stats.df$icprb_bioregion_id == "blue" & (stats.df$median_score >= 61.7 & stats.df$median_score< 82.2) ~ "fair",
    stats.df$icprb_bioregion_id == "blue" & (stats.df$median_score >= 82.2 & stats.df$median_score < 92.1) ~ "good",
    stats.df$icprb_bioregion_id == "blue" & stats.df$median_score >= 92.1 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "nrv" & stats.df$median_score < 19.1 ~ "very_poor",
    stats.df$icprb_bioregion_id == "nrv" & (stats.df$median_score >= 19.1 & stats.df$median_score < 38.2) ~ "poor",
    stats.df$icprb_bioregion_id == "nrv" & (stats.df$median_score >= 38.2 & stats.df$median_score < 50.8)~ "fair",
    stats.df$icprb_bioregion_id == "nrv" & (stats.df$median_score >= 50.8 & stats.df$median_score < 75.0) ~ "good",
    stats.df$icprb_bioregion_id == "nrv" & stats.df$median_score >= 75.0 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "srv" & stats.df$median_score < 21.6 ~ "very_poor",
    stats.df$icprb_bioregion_id == "srv" & (stats.df$median_score>= 21.6 & stats.df$median_score < 43.2) ~ "poor",
    stats.df$icprb_bioregion_id == "srv" & (stats.df$median_score>= 43.2 & stats.df$median_score < 58.0) ~ "fair",
    stats.df$icprb_bioregion_id == "srv" & (stats.df$median_score>= 58.0 & stats.df$median_score < 71.9) ~ "good",
    stats.df$icprb_bioregion_id == "srv" & stats.df$median_score>= 71.9 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "unp" & stats.df$median_score < 31.3 ~ "very_poor",
    stats.df$icprb_bioregion_id == "unp" & (stats.df$median_score >= 31.3 & stats.df$median_score < 62.6) ~ "poor",
    stats.df$icprb_bioregion_id == "unp" & (stats.df$median_score >= 62.6 & stats.df$median_score < 69.9) ~ "fair",
    stats.df$icprb_bioregion_id == "unp" & (stats.df$median_score >= 69.9 & stats.df$median_score < 80.5) ~ "good",
    stats.df$icprb_bioregion_id == "unp" & stats.df$median_score >= 80.5 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "sgv" & stats.df$median_score < 29.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "sgv" & (stats.df$median_score >= 29.9 & stats.df$median_score < 59.9) ~ "poor",
    stats.df$icprb_bioregion_id == "sgv" & (stats.df$median_score >= 59.9 & stats.df$median_score < 66.0) ~ "fair",
    stats.df$icprb_bioregion_id == "sgv" & (stats.df$median_score >= 66.0 & stats.df$median_score < 76.5) ~ "good",
    stats.df$icprb_bioregion_id == "sgv" & stats.df$median_score >= 76.5 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "lnp" & stats.df$median_score < 35.2 ~ "very_poor",
    stats.df$icprb_bioregion_id == "lnp" & (stats.df$median_score >= 35.2 & stats.df$median_score < 70.3) ~ "poor",
    stats.df$icprb_bioregion_id == "lnp" & (stats.df$median_score >= 70.3 & stats.df$median_score < 80.2) ~ "fair",
    stats.df$icprb_bioregion_id == "lnp" & (stats.df$median_score >= 80.2 & stats.df$median_score < 91.3) ~ "good",
    stats.df$icprb_bioregion_id == "lnp" & stats.df$median_score >= 91.3 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "pied" & stats.df$median_score < 30.3 ~ "very_poor",
    stats.df$icprb_bioregion_id == "pied" & (stats.df$median_score >= 30.3 & stats.df$median_score < 60.6) ~ "poor",
    stats.df$icprb_bioregion_id == "pied" & (stats.df$median_score >= 60.6 & stats.df$median_score < 73.2) ~ "fair",
    stats.df$icprb_bioregion_id == "pied" & (stats.df$median_score >= 73.2 & stats.df$median_score < 81.8) ~ "good",
    stats.df$icprb_bioregion_id == "pied" & stats.df$median_score >= 81.8 ~ "excellent",
    TRUE ~ "ERROR")
  stats.df$median_percent <- ((rowSums(stats.df[ , 103:202] == stats.df$median_rating))/100)*100
  stats.df$mean_score <- rowMeans((stats.df[ ,3:102]))
  stats.df$st_dev = apply(stats.df[ ,3:102],1, sd)
  stats.df$mean_rating <-
   case_when(
    stats.df$icprb_bioregion_id == "napu" & stats.df$mean_score < 17.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "napu" & (stats.df$mean_score >= 17.9 & stats.df$mean_score < 35.9) ~ "poor",
    stats.df$icprb_bioregion_id == "napu" & (stats.df$mean_score >= 35.9 & stats.df$mean_score < 47.4) ~ "fair",
    stats.df$icprb_bioregion_id == "napu" & (stats.df$mean_score >= 47.4 & stats.df$mean_score < 61.9) ~ "good",
    stats.df$icprb_bioregion_id == "napu" & stats.df$mean_score >= 61.9 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "nca" & stats.df$mean_score < 15.7 ~ "very_poor",
    stats.df$icprb_bioregion_id == "nca" & (stats.df$mean_score >= 15.7 & stats.df$mean_score < 31.5) ~ "poor",
    stats.df$icprb_bioregion_id == "nca" & (stats.df$mean_score >= 31.5 & stats.df$mean_score < 56.3) ~ "fair",
    stats.df$icprb_bioregion_id == "nca" & (stats.df$mean_score >= 56.3 & stats.df$mean_score < 78.7) ~ "good",
    stats.df$icprb_bioregion_id == "nca" & stats.df$mean_score >= 78.7 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "ca" & stats.df$mean_score < 27.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "ca" & (stats.df$mean_score >= 27.9 & stats.df$mean_score < 55.8) ~ "poor",
    stats.df$icprb_bioregion_id == "ca" & (stats.df$mean_score>= 55.8 & stats.df$mean_score < 69.5) ~ "fair",
    stats.df$icprb_bioregion_id == "ca" & (stats.df$mean_score>= 69.5 & stats.df$mean_score < 78.6)~ "good",
    stats.df$icprb_bioregion_id == "ca" & stats.df$mean_score>= 78.6 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "mac" & stats.df$mean_score < 22.7 ~ "very_poor",
    stats.df$icprb_bioregion_id == "mac" & (stats.df$mean_score>= 22.7 & stats.df$mean_score < 45.4) ~ "poor",
    stats.df$icprb_bioregion_id == "mac" & (stats.df$mean_score>= 45.4 & stats.df$mean_score < 63.2) ~ "fair",
    stats.df$icprb_bioregion_id == "mac" & (stats.df$mean_score>= 63.2 & stats.df$mean_score < 76.8) ~ "good",
    stats.df$icprb_bioregion_id == "mac" & stats.df$mean_score>= 76.8 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "sep" & stats.df$mean_score < 16.3 ~ "very_poor",
    stats.df$icprb_bioregion_id == "sep" & (stats.df$mean_score>= 16.3 & stats.df$mean_score < 32.6) ~ "poor",
    stats.df$icprb_bioregion_id == "sep" & (stats.df$mean_score>= 32.6 & stats.df$mean_score < 56.7) ~ "fair",
    stats.df$icprb_bioregion_id == "sep" & (stats.df$mean_score>= 56.7 & stats.df$mean_score < 83.9) ~ "good",
    stats.df$icprb_bioregion_id == "sep" & stats.df$mean_score>= 83.9 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "blue" & stats.df$mean_score < 30.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "blue" & (stats.df$mean_score >= 30.9 & stats.df$mean_score < 61.7) ~ "poor",
    stats.df$icprb_bioregion_id == "blue" & (stats.df$mean_score >= 61.7 & stats.df$mean_score< 82.2) ~ "fair",
    stats.df$icprb_bioregion_id == "blue" & (stats.df$mean_score >= 82.2 & stats.df$mean_score < 92.1) ~ "good",
    stats.df$icprb_bioregion_id == "blue" & stats.df$mean_score >= 92.1 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "nrv" & stats.df$mean_score < 19.1 ~ "very_poor",
    stats.df$icprb_bioregion_id == "nrv" & (stats.df$mean_score >= 19.1 & stats.df$mean_score < 38.2) ~ "poor",
    stats.df$icprb_bioregion_id == "nrv" & (stats.df$mean_score >= 38.2 & stats.df$mean_score < 50.8)~ "fair",
    stats.df$icprb_bioregion_id == "nrv" & (stats.df$mean_score >= 50.8 & stats.df$mean_score < 75.0) ~ "good",
    stats.df$icprb_bioregion_id == "nrv" & stats.df$mean_score >= 75.0 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "srv" & stats.df$mean_score < 21.6 ~ "very_poor",
    stats.df$icprb_bioregion_id == "srv" & (stats.df$mean_score>= 21.6 & stats.df$mean_score < 43.2) ~ "poor",
    stats.df$icprb_bioregion_id == "srv" & (stats.df$mean_score>= 43.2 & stats.df$mean_score < 58.0) ~ "fair",
    stats.df$icprb_bioregion_id == "srv" & (stats.df$mean_score>= 58.0 & stats.df$mean_score < 71.9) ~ "good",
    stats.df$icprb_bioregion_id == "srv" & stats.df$mean_score>= 71.9 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "unp" & stats.df$mean_score < 31.3 ~ "very_poor",
    stats.df$icprb_bioregion_id == "unp" & (stats.df$mean_score >= 31.3 & stats.df$mean_score < 62.6) ~ "poor",
    stats.df$icprb_bioregion_id == "unp" & (stats.df$mean_score >= 62.6 & stats.df$mean_score < 69.9) ~ "fair",
    stats.df$icprb_bioregion_id == "unp" & (stats.df$mean_score >= 69.9 & stats.df$mean_score < 80.5) ~ "good",
    stats.df$icprb_bioregion_id == "unp" & stats.df$mean_score >= 80.5 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "sgv" & stats.df$mean_score < 29.9 ~ "very_poor",
    stats.df$icprb_bioregion_id == "sgv" & (stats.df$mean_score >= 29.9 & stats.df$mean_score < 59.9) ~ "poor",
    stats.df$icprb_bioregion_id == "sgv" & (stats.df$mean_score >= 59.9 & stats.df$mean_score < 66.0) ~ "fair",
    stats.df$icprb_bioregion_id == "sgv" & (stats.df$mean_score >= 66.0 & stats.df$mean_score < 76.5) ~ "good",
    stats.df$icprb_bioregion_id == "sgv" & stats.df$mean_score >= 76.5 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "lnp" & stats.df$mean_score < 35.2 ~ "very_poor",
    stats.df$icprb_bioregion_id == "lnp" & (stats.df$mean_score >= 35.2 & stats.df$mean_score < 70.3) ~ "poor",
    stats.df$icprb_bioregion_id == "lnp" & (stats.df$mean_score >= 70.3 & stats.df$mean_score < 80.2) ~ "fair",
    stats.df$icprb_bioregion_id == "lnp" & (stats.df$mean_score >= 80.2 & stats.df$mean_score < 91.3) ~ "good",
    stats.df$icprb_bioregion_id == "lnp" & stats.df$mean_score >= 91.3 ~ "excellent",
    
    stats.df$icprb_bioregion_id == "pied" & stats.df$mean_score < 30.3 ~ "very_poor",
    stats.df$icprb_bioregion_id == "pied" & (stats.df$mean_score >= 30.3 & stats.df$mean_score < 60.6) ~ "poor",
    stats.df$icprb_bioregion_id == "pied" & (stats.df$mean_score >= 60.6 & stats.df$mean_score < 73.2) ~ "fair",
    stats.df$icprb_bioregion_id == "pied" & (stats.df$mean_score >= 73.2 & stats.df$mean_score < 81.8) ~ "good",
    stats.df$icprb_bioregion_id == "pied" & stats.df$mean_score >= 81.8 ~ "excellent",
    TRUE ~ "ERROR")
  stats.df$mean_percent <- ((rowSums(stats.df[ , 103:202] == stats.df$mean_rating))/100)*100 
  stats.df$rating_compare <- stats.df$median_rating == stats.df$mean_rating

ChessieBIBI_final <- stats.df
```
### **6. Final data frame**
Export the final data frame, **ChessieBIBI_final** as a CSV. Don't forget to change `name_of_file.csv` to another name.
```{r eval=FALSE, warning=F, message=F}
setwd("C:/Users/RJepson/OneDrive - ICPRB/Refining Chessie BIBI/Rerunning metrics on cleaned data")
write.csv(ChessieBIBI_final, "CBIBI_100_runs_cleaned_data_Apr2020.csv")
```
STUFF
```{r}
setwd("C:/Users/RJepson/Documents/ChessieBIBI_Final")
ids <- read.csv("unique_ids.csv")
library(tidyverse)
join <- left_join(ids, ChessieBIBI_final, by="unique_id")

setwd("C:/Users/RJepson/Documents/ChessieBIBI_Final")
write.csv(join, "final_correct_num.csv")

setwd("C:/Users/RJepson/Documents/ChessieBIBI_Final")
write.csv(metrics.key, "metrics.key.csv")

```


