---
title: "DREX_colors"
author: "Luke Vawter"
date: "August 29, 2018"
output: html_document
---

Working on 2018 DREX color quad display for Shenandoah and Northern Virginia.  Quads are:
precipitation, ground water wells, stream flow, reservoir flows.

Cherie will provide data for you to play with in 2018DREX/inputs repo.  

The code will consist of some basic control flow in R.
A basic example follows:

```{r}
# library(shiny)
# 
# ui <- fluidPage(
my_vec <- c(1,2,3,4,5,6,7,8,9,10,11,12)
for (i in my_vec) {
  if (i >= 0 && i < 3){
    color = "#e5e102"
    print(color)
  }
  else if (i >= 3 && i < 5){
    color = "#e5b702"
    print(color)
  }
  else if (i >= 5 && i < 7){
   color = "#e59502"
   print(color)
  }
  else if (i >= 7 && i < 9){
   color = "#e57702"
   print(color)
  }
  else if (i >= 9 && i < 11){
   color = "#e55102"
   print(color)
  }
  else if (i >= 11 && i <13){
    color = "#e52402"
    print(color)
  }
  else{
    color = "#000000"
    print(color)
  }
}





```
setting up a shiny app to adjust color output based on a slider with the same values as used above:

```{r}
library(shiny)

ui <- fluidPage(
  
  titlePanel("Slider to output test"),
  
  sidebarLayout(
    sidebarPanel(
      sliderInput(inputId = "color",
                  label = "HOW RED???",
                  min = 1, max = 13,
                  value = 4)
    
    ),
    mainPanel(
      plotOutput(outputId = "distPlot")
    )
  )
)

server <- function(input, output) {
  output$distPlot <- renderPlot({
    if (input$color >= 0 && input$color < 3){
    color = "#e5e102"
    }
    else if (input$color >= 3 && input$color < 5){
      color = "#e5b702"
    }
    else if (input$color >= 5 && input$color < 7){
     color = "#e59502"
    }
    else if (input$color >= 7 && input$color < 9){
     color = "#e57702"
    }
    else if (input$color >= 9 && input$color < 11){
     color = "#e55102"
    }
    else if (input$color >= 11 && input$color <13){
      color = "#e52402"
    }
    else{
      color = "#000000"
    }
    x    <- faithful$waiting
    bins <- seq(min(x), max(x), length.out = input$color + 1)

    hist(x, breaks = bins, col = color, border = "white",
         xlab = ":)",
         main = "Histogram of slider output")

  })
  
}

shinyApp(ui, server)
```
note: 4 colors.  Run the app and scroll to the bottom to see a mock-up map


A test of a datatable(to be continued after vacation):
```{r}
library("shiny")

ui <- fluidPage(
  fluidRow(
    column(8,
           sliderInput(inputId = "amount", 
                       label = "slide away",
                       value = 3, min = 1, max = 13)
           ),
    column(4,
           DT::dataTableOutput("table"))
  )
)

server <-function(output, input){
  output$table <- DT::renderDataTable(DT::datatable({
    
  }))
}

shinyApp(ui, server)
```


Toy code to grab data from 2018DREX/inputs/state:

```{r}
library(dplyr)

#some basic tests of grabbing csv data from DREX files, choosing a random value between 1 and list max range and returning basic info about the element at that index value

my_data = read.csv("C:\\Users\\icprbadmin\\Documents\\R\\2018drex\\input\\ts\\state\\i_a1b\\va_shenandoah_p.csv")
print(typeof(my_data))
#print(my_data)
limit <- length(my_data[[1]])
x <- sample(1:limit,1)
print(my_data$date[x])
print(my_data$p_percent_normal[x])
x <- sample(1:length(my_data),1)
#print(my_data)

```

Next I need to take the above code and adapt(for a percentage range, as above data) then apply the boolean logic from earlier:
```{r}
library(dplyr)

my_data = read.csv("C:\\Users\\icprbadmin\\Documents\\R\\2018drex\\input\\ts\\state\\i_a1b\\va_shenandoah_p.csv")

limit <- length(my_data[[1]])
random <- sample(1:limit,1)
data_percent <- my_data$p_percent_normal[random]

color <- case_when(
  data_percent <= .0 ~ "#000000",
  data_percent > .0 && data_percent <= .20 ~ "#cc3300",
  data_percent > .20 && data_percent <= .40 ~ "#ff9966",
  data_percent > .40 && data_percent <= .60 ~ "#ffcc00",
  data_percent > .60 && data_percent <= .80 ~"#99cc33",
  data_percent > .80 && data_percent < 1 ~ "#339900"
)
print(color)



```

note:final version will have 4 colors, not 5.  Data read code probably already exists in DREX so will need to use that pre-existing function(ask Cherie).

next I need to make a basic shinydashboard valuebox:
```{r}
library(shinydashboard)

ui <- dashboardPage(
  dashboardHeader(title = "test"),
  dashboardSidebar(),
    dashboardBody(
       fluidRow(
      box(valueBox(value = NULL, color = "navy", subtitle = NULL)))
    )
)

server <- function(input, output) {}

shinyApp(ui, server)
  
  
```
note: Valid colors are: red, yellow, aqua, blue, light-blue, green, navy, teal, olive, lime, orange, fuchsia, purple, maroon, black.

next step is to generate a simple box:
```{r}
library(shiny)
library(shinydashboard)
library(dplyr)

ui <- dashboardPage(
  dashboardHeader(title = "test"),
  dashboardSidebar(),
    dashboardBody(
       fluidRow(
      box(valueBoxOutput(outputId = "box"#, value = NULL, color = output$precip_value, subtitle = NULL
                         )))
    )
)

          
server <- function(input,output){
  path <- "C:\\Users\\icprbadmin\\Documents\\R\\2018drex\\input\\ts\\state\\i_a1b\\va_shenandoah_p.csv"

  #print(.Platform$OS.type)
  if( .Platform$OS.type == "unix" )
    path <- "/Users/lukevawter/Desktop/R/2018drex/input/ts/state/i_a1b/va_shenandoah_p.csv"

my_data = read.csv(path)
  output$box <- renderValueBox({
    limit <- length(my_data[[1]])
    random <- sample(1:limit,1)
    
    data_percent <- my_data$p_percent_normal[random]
    
  
    precip_value <- case_when(
      data_percent <= .0 ~ "purple", #"#000000",
      data_percent > .0 && data_percent <= .20 ~ "red", #"#cc3300",
      data_percent > .20 && data_percent <= .40 ~ "orange",  #"#ff9966",
      data_percent > .40 && data_percent <= .60 ~ "yellow",  #"#ffcc00",
      data_percent > .60 && data_percent <= .80 ~ "green", #"#99cc33",
      data_percent > .80 && data_percent < 1 ~  "navy" #"#339900"
      )
    valueBox(value = data_percent, color = precip_value, subtitle = "precip warning")
    
      
  
  
  }
)
}

shinyApp(ui, server)

```

adding a slider to scroll through elements in dataframe, and date as subtitle:
currently broken...fix next time
```{r}
library(shiny)
library(shinydashboard)
library(dplyr)

ui <- dashboardPage(
  dashboardHeader(title = "test"),
  dashboardSidebar(),
    dashboardBody(
      fluidRow(sliderInput(inputId = "data_index", 
            label = "test_slider", 
            value = 1, min = 1, max = 427)),
      box(valueBoxOutput(outputId = "box"
                         )
          )
    )
)

          
server <- function(input,output){
  path <- "C:\\Users\\icprbadmin\\Documents\\R\\2018drex\\input\\ts\\state\\i_a1b\\va_shenandoah_p.csv"

  if( .Platform$OS.type == "unix" )
    path <- "/Users/lukevawter/Desktop/R/2018drex/input/ts/state/i_a1b/va_shenandoah_p.csv"

  my_data = read.csv(path)

  limit <- length(my_data[[1]])
  #random <- sample(1:limit,1)
  current_index <- reactive({
    input$data_index
    })
  
  data_percent <- reactive({my_data$p_percent_normal[current_index]})
  data_date <- reactive({my_data$date[current_index]})
  
  #data_percent <- reactive({my_data$p_percent_normal[input$data_index]})
  #data_date <- reactive({my_data$date[input$data_index]})


  precip_value <- reactive({case_when(
    data_percent <= .0 ~ "purple", #"#000000",
    data_percent > .0 && data_percent <= .20 ~ "red", #"#cc3300",
    data_percent > .20 && data_percent <= .40 ~ "orange",  #"#ff9966",
    data_percent > .40 && data_percent <= .60 ~ "yellow",  #"#ffcc00",
    data_percent > .60 && data_percent <= .80 ~ "green", #"#99cc33",
    data_percent > .80 && data_percent < 1 ~  "navy" #"#339900"
    )
  })
  output$box <- renderValueBox({
    valueBox(value = data_percent, color = precip_value, subtitle = data_date)
  })
}

shinyApp(ui, server)

```
https://stackoverflow.com/questions/20456694/grid-of-responsive-squares
has a nice guide for creating html squares with reactive content:

9/14/18
looks as though the Cairo package may have some issues on Mac(working from home today and it popped up so and trying to resolve it):
```{r}
library(shiny)
library(Cairo)


```
returns an error...

but since final product only needs to run on Cherie's machine(not a linux one) I'll just work on a windows machine when working on DREX

next problem is filepaths issues when on a new system(windows to linux here).  Since this issue is likely to pop up often, and the fix looks doable, I'll spend a bit of time to attempt to resolve.  Solution below is apadted from and borrows heavily from the solution at https://stackoverflow.com/questions/22423020/detect-os-and-change-the-path-appropriately-in-r:
```{r}
#Sys.info()
  #my_data = read.csv("C:\\Users\\icprbadmin\\Documents\\R\\2018drex\\input\\ts\\state\\i_a1b\\va_shenandoah_p.csv")
  #my_data = read.csv("/Users/lukevawter/Desktop/R/2018drex/input/ts/state/i_a1b/va_shenandoah_p.csv")
 
path <- "C:\\Users\\icprbadmin\\Documents\\R\\2018drex\\input\\ts\\state\\i_a1b\\va_shenandoah_p.csv"

 print(.Platform$OS.type)
if( .Platform$OS.type == "unix" )
  path <- "/Users/lukevawter/Desktop/R/2018drex/input/ts/state/i_a1b/va_shenandoah_p.csv"

my_data = read.csv(path)
#setwd( path )

print(my_data)
```
with this solved I can keep building up the toy model of DREX components in DREX_toy_colors.Rmd and Shiny_test_app.Rmd
