---
title: "DREX_colors"
author: "Luke Vawter"
date: "August 29, 2018"
output: html_document
---

Working on 2018 DREX color quad display for Shenandoah and Northern Virginia.  Quads are:
precipitation, ground water wells, stream flow, reservoir flows.

Cherie will provide data for you to play with in 2018DREX/inputs repo.  

The code will consist of some basic control flow in R.
A basic example follows:

```{r}
# library(shiny)
# 
# ui <- fluidPage(
my_vec <- c(1,2,3,4,5,6,7,8,9,10,11,12)
for (i in my_vec) {
  if (i >= 0 && i < 3){
    color = "#e5e102"
    print(color)
  }
  else if (i >= 3 && i < 5){
    color = "#e5b702"
    print(color)
  }
  else if (i >= 5 && i < 7){
   color = "#e59502"
   print(color)
  }
  else if (i >= 7 && i < 9){
   color = "#e57702"
   print(color)
  }
  else if (i >= 9 && i < 11){
   color = "#e55102"
   print(color)
  }
  else if (i >= 11 && i <13){
    color = "#e52402"
    print(color)
  }
  else{
    color = "#000000"
    print(color)
  }
}





```
setting up a shiny app to adjust color output based on a slider with the same values as used above:

```{r}
library(shiny)

ui <- fluidPage(
  
  titlePanel("Slider to output test"),
  
  sidebarLayout(
    sidebarPanel(
      sliderInput(inputId = "color",
                  label = "HOW RED???",
                  min = 1, max = 13,
                  value = 4)
    
    ),
    mainPanel(
      plotOutput(outputId = "distPlot")
    )
  )
)

server <- function(input, output) {
  output$distPlot <- renderPlot({
    if (input$color >= 0 && input$color < 3){
    color = "#e5e102"
    }
    else if (input$color >= 3 && input$color < 5){
      color = "#e5b702"
    }
    else if (input$color >= 5 && input$color < 7){
     color = "#e59502"
    }
    else if (input$color >= 7 && input$color < 9){
     color = "#e57702"
    }
    else if (input$color >= 9 && input$color < 11){
     color = "#e55102"
    }
    else if (input$color >= 11 && input$color <13){
      color = "#e52402"
    }
    else{
      color = "#000000"
    }
    x    <- faithful$waiting
    bins <- seq(min(x), max(x), length.out = input$color + 1)

    hist(x, breaks = bins, col = color, border = "white",
         xlab = ":)",
         main = "Histogram of slider output")

  })
  
}

shinyApp(ui, server)
```
note: 4 colors.  Run the app and scroll to the bottom to see a mock-up map


A test of a datatable(to be continued after vacation):
```{r}
library("shiny")

ui <- fluidPage(
  fluidRow(
    column(8,
           sliderInput(inputId = "amount", 
                       label = "slide away",
                       value = 3, min = 1, max = 13)
           ),
    column(4,
           DT::dataTableOutput("table"))
  )
)

server <-function(output, input){
  output$table <- DT::renderDataTable(DT::datatable({
    
  }))
}

shinyApp(ui, server)
```


Toy code using data from 2018DREX/inputs/state:

```{r}
print("code coming soon")
```

